### 2016-09-18 infdebruijn.tex
First version

\documentclass{article}
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}

%\IEEEoverridecommandlockouts        % This command is only needed if you want to use the \thanks command
%\overrideIEEEmargins                        % See the \addtolength command later in the file to balance the column lengths

% Name clashes workaround
%\makeatletter
%\let\IEEEproof\proof
%\let\IEEEendproof\endproo f
%\let\proof\@undefined
%\let\endproof\@undefined
%\makeatother

\usepackage{epsfig} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}  
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{automata,arrows,decorations.pathmorphing,decorations.markings,positioning}
\usetikzlibrary{shapes}
%\usepackage{balance}

% Theorem like env.
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}

\theoremstyle{definition}
\newtheorem{definition}{Definition}     
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{corrolary}[theorem]{Corrolary}

%------------------------------------------- preamble ---------------------------

\newcommand{\R}{{\mathbb{R}}}
\newcommand{\N}{{\mathbb{N}}}
\newcommand{\C}{{\mathbb{C}}}
\newcommand{\Z}{{\mathbb{Z}}}

\newcommand{\REF}[2]{#1~\ref{#2}}

\newcommand{\T}[1]{\langle{#1}\rangle}
\newcommand{\rr}[2]{R^{#2}({#1})}
\newcommand{\rl}[2]{R^{-{#2}}({#1})}

\newcommand{\AorB}[2]{\bigl(#2\text{?}A(#1)\text{:}B(#1)\bigr)}

\pagestyle{plain}

\title{On Combinatorial Games and de Bruijn Sequences}

\author{Yotam Svoray and %Gera Weiss\\
	Department of Computer Science \\
	Ben Gurion University of the Negev\\
	Israel
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

	%\section{Results}

\begin{definition}
For a parameter $n$, Let $L \subset \N^+$ be the set of non-periodic words over the alphabet $\Sigma=\N$ that are bigger in Arabic (right-to-left) lexicographical order than all of their rotations. Let $L_n$ be the set of all the words in $L$ whose length divides $n$.
\end{definition}

\begin{definition}\label{forward}
For a word $w$ whose length is smaller or equal than $n$, let  $f(w)$ be the transformation defined by successive applications of the following steps to $w$:
\begin{enumerate}
	\item[$f_1$:] Increase the first letter of the word by one. 
	\item[$f_2$:] Pad with zeros on the left to get a word of length $n$.
	\item[$f_3$:] Apply the substitution rules $u(vu)^+ \mapsto vu$ and then $w^+ \mapsto w$, with the longest possible $u$ and the shortest possible $w$.
\end{enumerate}
\end{definition}

\begin{definition}\label{backward}
For a a word $w$ whose length is smaller or equal than $n$, let  $b(w)$ be the transformation defined by successive applications of the following steps to $w$:
\begin{enumerate}
	\item[$b_1$:] Expand $w$ to $u w^m$ where $m=\lfloor n/ |w| \rfloor$ and $u$ is the prefix of length $n-m|w|$ of $w$.

	\item[$b_2$:] Remove leading zeros.
	\item[$b_3$:] Decrease the first letter by one.
\end{enumerate}
\end{definition}

\begin{observation}
	For any $w\in L_n$, $f(b(w))=b(f(w))=w$.
\end{observation}

\begin{proposition}
	If we start with $w(0)=0$ and generate a sequence of words by $w({i+1})=f(w(i))$, we get an enumeration of all the words in $L$ whose length divides $n$.
\end{proposition}
\begin{proof}
	This is a version of Duval's algorithm with a reversed order of the alphabet and a reversed order of letters in a word.
\end{proof}

\begin{definition}
	Let $f^*(w)$ be the first word in ${f(w),f(f(w)),\dots}$ whose length divides $n$ and let $b^*(w)$ be the first word in ${b(w),b(b(w)),\dots}$ whose length divides $n$. 
\end{definition}

%\begin{observation}
%	$b(w)$ is a suffix of $b^*(w)$ for every $w \in L_n$.
%\end{observation}
%\begin{proof}
%	If $|b(w)|$ is not $n$, then $b_1(b(w))$ gives a word of length $n$ that ends with $b(w)$. Since
%\end{proof}

\begin{definition}
	Let $w(0),w(1),...$ be the sequence generated by starting with $w(0)=0$ and then continuing ad infinitum by $w{(i+1)}=f^*(w(i))$ and let $w^*$ be the infinite word obtained by concatenating all these words.
\end{definition}

\begin{definition}
	For a word $w=\sigma_1\cdots\sigma_{n-1}\sigma_n$ let  $\rr{w}{}= \sigma_{n}\sigma_1\cdots\sigma_{n-1}$ be the rotation of $w$ to the right. Then, the nested invocation $\rr{w}{m}$ is the $m$ letter rotation to the right and its inverse $\rl{w}{m}$ is the $m$ letter rotation to the left.
\end{definition}

\begin{proposition}\label{simple-pos}
	For a $w \in L_n$ let $l$ be the number of trailing zeros (from the left) in $w$ and $\bar{w}=b_1(w)$. Then:
	\begin{enumerate}
		\item For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes exactly $i$ letters before $w$ as a sub-word of $w^*$.

		\item For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes as sub-words of $w^*$ exactly $i-\operatorname{mod}(n-|f_3(u)|,n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
	\end{enumerate}
\end{proposition}

\begin{proposition}
	The word $w^*$ contains all the words in $\N^n$ as subwords.
\end{proposition}
\begin{proof}
	Any word is a rotation of the expansion of some word in $L$.
\end{proof}

\begin{proposition}
	For any $k$ the prefix $w^*_1 \cdots w^*_{k^n}$ is an $n$-order de Bruijn sequences. Moreover, it is the reversed of the n-order prefer-max sequence on the alphabet $\T{0,\dots,k-1}$ (in this order). 
\end{proposition}
\begin{proof}
	Counting argument + arguing that if $|w| =n-1$ and $\sigma_1 < \sigma_2$ then $w\sigma_1$ comes before $w\sigma_2$ as subwords of $w^*$.
\end{proof}

\begin{proposition}
	For $w \in \N^n$, let $i$ be the minimal index such that $\rl{w}{i} \in L$ and let $\bar{w}=\rl{w}{i}$. Let $\bar{w}^+=\bar{w}_{1..i}(\bar{w}_{i+1}+1)\bar{w}_{(i+2)..n}$, i.e., the word obtained by increasing the $(i+1)th$ letter of $\bar{w}$ by one.  Then, the function
	$$next(w)=
	\begin{cases}
	f^*(f_3(w))_1 & \text{if } w \in L; \\
	w_1+1         & \text{if }\bar{w}_{1..i}= 0^i \wedge \bar{w}^+ \in L\wedge \max{(\bar{w}^+_{1..(n-1)})} \leq \max(w); \\
	0             & \text{if }\bar{w}_{1..i}= 0^i \wedge (\bar{w}^+ \notin L \vee \max{(\bar{w}^+_{1..(n-1)})} > \max(w)); \\
	w_1           & \text{otherwise.}
	\end{cases}$$
	represents the mapping of a word $w$ to the letter that follows the (only) occurrence of $w$ as a subword of $w^*$.
\end{proposition}

\begin{definition}
	Let $w(0)=0, w(1)=f^*(w(0)),\dots,w(i)=f^*(w{(i-1)}),\dots$ be our enumeration of all the words in $L_n$. Let $w^{(i)}$ be the concatenation of the first $i$ words in this enumeration and let $u(j)=w^{(i)}_{j-n+1}\cdots w^{(i)}_j$ be the ``window'' of length $n$ before the $j$th letter in $w^{(i)}$.
\end{definition}

\begin{proposition}
	For a word $w=w(i)$ be the $i$th word in the above enumeration. Let $l$ be the number of leading zeros in $w$ and let $\hat{w}=\rl{b_1(b^*(w)}{l}$. Then, inserting the cycle $\T{\rl{b_1(w)}{s}}_{s=0}^{n-1}$ after the word $\hat{w}_{1..(n-l)}0^l$ in $\T{u(j)}_{j=0}^{i-1}$ yields the sequence $\T{u(j)}_{j=0}^{i}$.
\end{proposition}

\end{document}

### 2016-09-20 infdebruijn.tex
.

@@
 \begin{enumerate}
-	\item[$b_1$:] Expand $w$ to $u w^m$ where $m=\lfloor n/ |w| \rfloor$ and $u$ is the prefix of length $n-m|w|$ of $w$.
+	\item[$b_1$:] Expand $w$ to $u w^m$ where $m=\lfloor n/ |w| \rfloor$ and $u$ is the suffix of length $n-m|w|$ of $w$.
 
@@
 \begin{proposition}
-	If we start with $w(0)=0$ and generate a sequence of words by $w({i+1})=f(w(i))$, we get an enumeration of all the words in $L$ whose length divides $n$.
+	If we start with $w(0)=0$ and generate a sequence of words by $w({i+1})=f(w(i))$, we get an enumeration of all the words in $L$ whose length in smaller or equal to $n$.
 \end{proposition}
@@
 \begin{definition}
-	Let $w(0),w(1),...$ be the sequence generated by starting with $w(0)=0$ and then continuing ad infinitum by $w{(i+1)}=f^*(w(i))$ and let $w^*$ be the infinite word obtained by concatenating all these words.
+	Let $w(0),w(1),...$ be the sequence generated by starting with $w(0)=0$ and then continuing ad infinitum by $w{(i+1)}=f^*(w(i))$ and let $w^\infty$ be the infinite word obtained by concatenating all the words in this sequence.
 \end{definition}
@@
 	\begin{enumerate}
-		\item For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes exactly $i$ letters before $w$ as a sub-word of $w^*$.
+		\item For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i$ letters before $w$ as a sub-word of $w^\infty$.
 
-		\item For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes as sub-words of $w^*$ exactly $i-\operatorname{mod}(n-|f_3(u)|,n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
+		\item For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
 	\end{enumerate}
@@
 \begin{proposition}
-	The word $w^*$ contains all the words in $\N^n$ as subwords.
+	The word $w^\infty$ contains all the words in $\N^n$ as subwords.
 \end{proposition}
 \begin{proof}
-	Any word is a rotation of the expansion of some word in $L$.
+	Any word of length $n$ is a rotation of the expansion of a word in $L_n$.
 \end{proof}
@@
 \begin{proposition}
-	For any $k$ the prefix $w^*_1 \cdots w^*_{k^n}$ is an $n$-order de Bruijn sequences.
+	For any $k$ the prefix $w^\infty_1 \cdots w^\infty_{k^n}$ is an $n$-order de Bruijn sequences.
 Moreover, it is the reversed of the n-order prefer-max sequence on the alphabet $\T{0,\dots,k-1}$ (in this order).
@@
 \begin{proof}
-	Counting argument + arguing that if $|w| =n-1$ and $\sigma_1 < \sigma_2$ then $w\sigma_1$ comes before $w\sigma_2$ as subwords of $w^*$.
+	Counting argument + arguing that if $|w| =n-1$ and $\sigma_1 < \sigma_2$ then $w\sigma_1$ comes before $w\sigma_2$ as subwords of $w^\infty$.
 \end{proof}
@@
 	\end{cases}$$
-	represents the mapping of a word $w$ to the letter that follows the (only) occurrence of $w$ as a subword of $w^*$.
+	represents the mapping of a word $w$ to the letter that follows the (one and only) occurrence of $w$ as a subword of $w^\infty$.
 \end{proposition}
@@
 	Let $w(0)=0, w(1)=f^*(w(0)),\dots,w(i)=f^*(w{(i-1)}),\dots$ be our enumeration of all the words in $L_n$.
-Let $w^{(i)}$ be the concatenation of the first $i$ words in this enumeration and let $u(j)=w^{(i)}_{j-n+1}\cdots w^{(i)}_j$ be the ``window'' of length $n$ before the $j$th letter in $w^{(i)}$.
+Let $w^{(i)}=w(0)\cdots w(i)$ be the concatenation of the first $i$ words in this enumeration and let $u(j)=w^{(i)}_{j-n+1}\cdots w^{(i)}_j$ be the ``window'' of length $n$ before the $j$th letter in $w^{(i)}$.
 \end{definition}

### 2016-09-20 infdebruijn.tex
Fixed an error in the statement of Proposition~\ref{simple-pos}

@@
 
-%\begin{observation}
-%	$b(w)$ is a suffix of $b^*(w)$ for every $w \in L_n$.
-%\end{observation}
-%\begin{proof}
-%	If $|b(w)|$ is not $n$, then $b_1(b(w))$ gives a word of length $n$ that ends with $b(w)$. Since
-%\end{proof}
-
 \begin{definition}
@@
 \begin{proposition}\label{simple-pos}
-	For a $w \in L_n$ let $l$ be the number of trailing zeros (from the left) in $w$ and $\bar{w}=b_1(w)$. Then:
-	\begin{enumerate}
-		\item For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i$ letters before $w$ as a sub-word of $w^\infty$.
+	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$.
+Then For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i+n-|w|$ letters before $w$ as a sub-word of $w^\infty$.
+\end{proposition}
+\begin{proof}
+	Let $v=b(w)$.
+Looking at the definition of $b$, it is easy to see that the last $l-1$ letters of $w$ are not changed by the transformation, i.e., $v_{|v|-l-2}\cdots v_{|v|}=w_{|w|-l-2} \cdots w_{|w|}$.
+Furthermore, if the length of $w$ is not $n$, the previous letter does not change either, $v_{|v|-l-1}=w_{|v|-l-1}$, because $b$ expands the word by a prefix that is not all zeros before it decreases the first letter.
+Since $b^*$ consists of repeated applications of $b$ until the length of the resulting word divides $n$, we get that only the first application of $b$ may change the first letter of the tail of length $l$ of $w$ and that the rest of the applications of $b$ keep this tail fixed.
+Thus the word that precedes $w$ in the sequence shares the tail of length $l-1$ with $w$, i.e., all the windows of the required form appear just before $w$.
+\end{proof}
 
-		\item For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
-	\end{enumerate}
+\begin{proposition}\label{advanced-pos}
+	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$.
+Then For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
 \end{proposition}

### 2016-09-28 infdebruijn.tex
.

@@
 
+\begin{observation}
+	\label{tail-is-preserved}
+	For any $w=0^lw_{m-l}\cdots w_{m-1} w_m \in L_n$ where $w_{m-l} \neq 0$ and for each $0 \leq i < l$ we have  $b(w)_{|b(w)|-i}=w_{m-i}$.
+If, in addition, $m \neq n$ we also have $b(w)_{|b(w)|-l} = w_{m-l}$.
+\end{observation}
+
 \begin{proposition}
@@
 \begin{definition}
-	Let $f^*(w)$ be the first word in ${f(w),f(f(w)),\dots}$ whose length divides $n$ and let $b^*(w)$ be the first word in ${b(w),b(b(w)),\dots}$ whose length divides $n$. 
+	Let $f^*(w)$ be the first word in ${f(w),f(f(w)),\dots}$ whose length divides $n$ and, similarly, let $b^*(w)$ be the first word in ${b(w),b(b(w)),\dots}$ whose length divides $n$. 
 \end{definition}
+
+\begin{observation} \label{tail-is-preserved-by-bstart}
+	Observation~\ref{tail-is-preserved} is true also when we replace $b$ with $b^*$. 
+\end{observation}
+\begin{proof}
+We only apply $b$ again if the length is not $n$, so after the first application of $b$, that may change the first letter in the tail $w_{m-1}\cdots w_m$ when the length of $w$ is $n$, the tail remains as it is.
+\end{proof}
 
@@
 \begin{definition}
-	For a word $w=\sigma_1\cdots\sigma_{n-1}\sigma_n$ let  $\rr{w}{}= \sigma_{n}\sigma_1\cdots\sigma_{n-1}$ be the rotation of $w$ to the right.
+	For a word $w=w_1\cdots w_{n-1}w_n$ let  $\rr{w}{}= w_{n}w_1\cdots w_{n-1}$ be the rotation of $w$ to the right.
 Then, the nested invocation $\rr{w}{m}$ is the $m$ letter rotation to the right and its inverse $\rl{w}{m}$ is the $m$ letter rotation to the left.
@@
 \begin{proof}
-	Let $v=b(w)$.
-Looking at the definition of $b$, it is easy to see that the last $l-1$ letters of $w$ are not changed by the transformation, i.e., $v_{|v|-l-2}\cdots v_{|v|}=w_{|w|-l-2} \cdots w_{|w|}$.
-Furthermore, if the length of $w$ is not $n$, the previous letter does not change either, $v_{|v|-l-1}=w_{|v|-l-1}$, because $b$ expands the word by a prefix that is not all zeros before it decreases the first letter.
-Since $b^*$ consists of repeated applications of $b$ until the length of the resulting word divides $n$, we get that only the first application of $b$ may change the first letter of the tail of length $l$ of $w$ and that the rest of the applications of $b$ keep this tail fixed.
-Thus the word that precedes $w$ in the sequence shares the tail of length $l-1$ with $w$, i.e., all the windows of the required form appear just before $w$.
+	If the length of $w$ is $n$ then $\bar{w}=w$ and, by Observation~\ref{tail-is-preserved-by-bstart}, the word that precedes $w$ ends with the last $l-1$ letters of $w$.
+In particular, the word $\rr{\bar{w}}{i}$ comes $i$ letters before $w$ as claimed.
+
 \end{proof}

### 2016-09-29 infdebruijn.tex
.

@@
 
-\begin{observation}
-	\label{tail-is-preserved}
-	For any $w=0^lw_{m-l}\cdots w_{m-1} w_m \in L_n$ where $w_{m-l} \neq 0$ and for each $0 \leq i < l$ we have  $b(w)_{|b(w)|-i}=w_{m-i}$.
-If, in addition, $m \neq n$ we also have $b(w)_{|b(w)|-l} = w_{m-l}$.
-\end{observation}
-
 \begin{proposition}
@@
 
-\begin{observation} \label{tail-is-preserved-by-bstart}
-	Observation~\ref{tail-is-preserved} is true also when we replace $b$ with $b^*$. 
-\end{observation}
+\begin{proposition}
+	\label{w-at-the-tail}
+	If $w \in L_n$ and $|w| \neq n$ then  $b(w)=uw$ for some non-empty word $u$. 
+\end{proposition}
 \begin{proof}
-We only apply $b$ again if the length is not $n$, so after the first application of $b$, that may change the first letter in the tail $w_{m-1}\cdots w_m$ when the length of $w$ is $n$, the tail remains as it is.
+	The first transformation $b_1$ extends $w$ to the left producing the word $b_1(w)=uw^m$ where $u$ is a tail of $w$.
+Since $w \in L_n$ and because it contains a letter $\sigma$ that is not zero, we have, by maximality of $w$ among its rotations in right-to-left lexicographical order,  that its last letter is not zero.
+The last letter of $u$ is the last letter of $w$ so it is also not zero.
+This gives us that the next transformation $b_2$, that deletes trailing zeros, leaves at least the last copy of $w$ and the last letter of the before-last (full or partial) copy at the tail of $b_1(w)$.
+Thus, $b_2(b_1(w))=uw$ where $u$ is a non-empty word whose first letter is not zero.
+Then, the last transformation $b_3$ only decreases the first letter of $u$ by  one which gives us that $b(w)=b_3(b_2(b_1(w)))=vw$ for some non-empty word $v$.
+\end{proof}
+
+\begin{proposition}
+	\label{tail-is-preserved}
+	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a word that ends with a non-zero letter there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
+\end{proposition}
+\begin{proof}
+	If $|w|\neq n$ the proof follows by Proposition~\ref{w-at-the-tail}. If $|w|=n$ then $b_1(w)=w$, $b_2(b_1(w))=\sigma\hat{w}$, and $b_3(b_2(b_1(w)))=(\sigma-1)\hat{w}$ and the claim follows as well.
+\end{proof}
+
+\begin{proposition}
+	\label{tail-is-preserved}
+	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a word that ends wit a non-zero letter is a non-empty word $u$ such that $b^*(w)=u\hat{w}$.
+\end{proposition}
+\begin{proof}
+Let $w{(1)}=b(w), w{(2)}=b(w{(1)}),\dots,w{(m)}=b(w{(m-1)})$ such that $m$ is the first index such that $|w{(m)}|$ divides $n$, i.e., let $w{(1)},\dots,w{(m)}$ be the intermediate words in the computation of $b^*(w)$.
+
+We only apply $b$ again if the length is not $n$, so the tail remains as it is after the first application of $b$, that may change the first letter in the tail $w_{m-1}\cdots w_m$ when the length of $w$ is $n$.
 \end{proof}

### 2016-09-29 infdebruijn.tex
.

@@
 \begin{proposition}
-	\label{tail-is-preserved}
-	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a word that ends with a non-zero letter there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
+	\label{hat-w-at-the-tail}
+	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
 \end{proposition}
@@
 \begin{proposition}
-	\label{tail-is-preserved}
-	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a word that ends wit a non-zero letter is a non-empty word $u$ such that $b^*(w)=u\hat{w}$.
+	\label{tail-is-preserved*}
+	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b^*(w)=u\hat{w}$.
 \end{proposition}
 \begin{proof}
-Let $w{(1)}=b(w), w{(2)}=b(w{(1)}),\dots,w{(m)}=b(w{(m-1)})$ such that $m$ is the first index such that $|w{(m)}|$ divides $n$, i.e., let $w{(1)},\dots,w{(m)}$ be the intermediate words in the computation of $b^*(w)$.
-
-We only apply $b$ again if the length is not $n$, so the tail remains as it is after the first application of $b$, that may change the first letter in the tail $w_{m-1}\cdots w_m$ when the length of $w$ is $n$.
+By definition, $b^*$ consists of repeated applications of $b$ until a word whose length devides $n$ is obtained.
+In particular, only the first of these applications of $b$ act on a parameter whose length may be $n$.
+By Proposition~\ref{hat-w-at-the-tail}, this first application produces a word that ends with $\hat{w}$ and by Proposition~\ref{w-at-the-tail} each of the remaining applications only add prefixes.
 \end{proof}
@@
 	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$.
-Then For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i+n-|w|$ letters before $w$ as a sub-word of $w^\infty$.
+Then, for all $0 \leq i \leq |w|-l-1$, the word $\rr{\bar{w}}{i}$ comes $i+n-|w|$ letters before $w$ as a sub-word of $w^\infty$.
 \end{proposition}
 \begin{proof}
-	If the length of $w$ is $n$ then $\bar{w}=w$ and, by Observation~\ref{tail-is-preserved-by-bstart}, the word that precedes $w$ ends with the last $l-1$ letters of $w$.
-In particular, the word $\rr{\bar{w}}{i}$ comes $i$ letters before $w$ as claimed.
-
+	By Proposition~\ref{tail-is-preserved*} the words that come before $w$ ends with the last $|w|-l$ letters of $w$.
+In particular, the $n$ letter word that starts $i+n-|w|$ before $w$ is $\rr{\bar{w}}{i}$.
 \end{proof}

### 2016-09-29 infdebruijn.tex
.

@@
 	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$.
-Then For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
+Then, for all $|w|-l \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i+1}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
 \end{proposition}

### 2016-10-05 infdebruijn.tex
.

@@
 
-	%\section{Results}
-
 \begin{definition}
@@
 \end{definition}
+
+\begin{definition}
+	For a word $w=w_1\cdots w_{n-1}w_n$ let  $\rr{w}{}= w_{n}w_1\cdots w_{n-1}$ be the rotation of $w$ to the right.
+Then, the nested invocation $\rr{w}{m}$ is the $m$ letter rotation to the right and its inverse $\rl{w}{m}$ is the $m$ letter rotation to the left.
+\end{definition}
+
+\section{Forward and backwards transformations}
 
@@
 \begin{proposition}
-	If we start with $w(0)=0$ and generate a sequence of words by $w({i+1})=f(w(i))$, we get an enumeration of all the words in $L$ whose length in smaller or equal to $n$.
+	If we start with $w(0)=0$ and generate a sequence of words by $w({i+1})=f(w(i))$, we get an enumeration of all the words in $L$ whose length is smaller or equal to $n$.
 \end{proposition}
@@
 
-\begin{definition}
+\begin{definition} \label{star-functions}
 	Let $f^*(w)$ be the first word in ${f(w),f(f(w)),\dots}$ whose length divides $n$ and, similarly, let $b^*(w)$ be the first word in ${b(w),b(b(w)),\dots}$ whose length divides $n$. 
 \end{definition}
+
+\begin{definition}
+	Let $w(0),w(1),...$ be the sequence generated by starting with $w(0)=0$ and then continuing ad infinitum by $w{(i+1)}=f^*(w(i))$ and let $w^\infty\in \N^\omega$ be the concatenation of all these words.
+\end{definition}
+
+\section{Where can I find $w$ as a sub-word of $w^\infty$?}
+
+In this section we point at the position of an arbitrary word $w$ as a sub-word of  $w^\infty$ relative to the position of the a corresponding word in $L_n$.
+This is given in Proposition~\ref{simple-pos} and in Proposition~\ref{advanced-pos}.
+Towards the proofs of these propositions, we first establish some technical results about the functions $b$ and $b^*$ specified, respectively, in Definition~\ref{backward} and in Definition~\ref{star-functions}.
 
@@
 
-\begin{definition}
-	Let $w(0),w(1),...$ be the sequence generated by starting with $w(0)=0$ and then continuing ad infinitum by $w{(i+1)}=f^*(w(i))$ and let $w^\infty$ be the infinite word obtained by concatenating all the words in this sequence.
-\end{definition}
-
-\begin{definition}
-	For a word $w=w_1\cdots w_{n-1}w_n$ let  $\rr{w}{}= w_{n}w_1\cdots w_{n-1}$ be the rotation of $w$ to the right.
-Then, the nested invocation $\rr{w}{m}$ is the $m$ letter rotation to the right and its inverse $\rl{w}{m}$ is the $m$ letter rotation to the left.
-\end{definition}
+\begin{proposition}\label{simple-pos}
+	Let $w$ be an arbitrary word in $\N^n$ and let and let $\bar{w}=f_3(w)$.
+Let $l$ be the (possibly zero) number of trailing zeros (from the left) in $w$.
+Then, for all $0 \leq i \leq |w|-l-1$, the word $\rr{\bar{w}}{i}$ comes $i+n-|w|$ letters before $w$ as a sub-word of $w^\infty$.
+\end{proposition}
 

### 2016-10-27 infdebruijn.tex
aaa
.

@@
 	\label{hat-w-at-the-tail}
-	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
+	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
 \end{proposition}
@@
 	If $|w|\neq n$ the proof follows by Proposition~\ref{w-at-the-tail}. If $|w|=n$ then $b_1(w)=w$, $b_2(b_1(w))=\sigma\hat{w}$, and $b_3(b_2(b_1(w)))=(\sigma-1)\hat{w}$ and the claim follows as well.
-\end{proof}
-
-\begin{proposition}
-	\label{tail-is-preserved*}
-	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b^*(w)=u\hat{w}$.
-\end{proposition}
-\begin{proof}
-By definition, $b^*$ consists of repeated applications of $b$ until a word whose length devides $n$ is obtained.
-In particular, only the first of these applications of $b$ act on a parameter whose length may be $n$.
-By Proposition~\ref{hat-w-at-the-tail}, this first application produces a word that ends with $\hat{w}$ and by Proposition~\ref{w-at-the-tail} each of the remaining applications only add prefixes.
 \end{proof}

### 2016-10-27 infdebruijn.tex
.

@@
 \begin{proof}
-	By Proposition~\ref{tail-is-preserved*} the words that come before $w$ ends with the last $|w|-l$ letters of $w$.
+	By Proposition~\ref{tail-is-preseved*} the words that come before $w$ ends with the last $|w|-l$ letters of $w$.
 In particular, the $n$ letter word that starts $i+n-|w|$ before $w$ is $\rr{\bar{w}}{i}$.
@@
 	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$.
-Then, for all $|w|-l \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i+1}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
+Then, for all $|w|-l \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i+1}^{n}$ that is in $L_n$.
 \end{proposition}

### 2016-11-02 infdebruijn.tex
bla bla

--- 2016-10-05 infdebruijn.tex
@@
 	For a word $w=w(i)$ be the $i$th word in the above enumeration.
-Let $l$ be the number of leading zeros in $w$ and let $\hat{w}=\rl{b_1(b^*(w)}{l}$.
+Let $l$ be the number of leading zeros in $w$ and let $\hat{w}=\rl{b_1(b^*(w))}{l}$.
 Then, inserting the cycle $\T{\rl{b_1(w)}{s}}_{s=0}^{n-1}$ after the word $\hat{w}_{1..(n-l)}0^l$ in $\T{u(j)}_{j=0}^{i-1}$ yields the sequence $\T{u(j)}_{j=0}^{i}$.
@@
 
+\section{Where can I find $w$ as a sub-word of $w^\infty$? (second try...)}
+
+\begin{definition}
+For a word $w$, $max(w)$ is the maximal digit in $w$.
+\end{definition}
+
+\begin{definition}
+A word $u\in \mathbb{N}$ corresponds to $w\in L_n$ if $u$ is a rotation of $w^{\frac{n}{|w|}}$. Note that each $u\in \mathbb{N}$ corresponds to exactly one word $w\in L_n$.
+\end{definition}
+
+\begin{proposition}
+\label{newforward}
+If $w\in L_n$ and $|w|<n$, then $f^*(w)=f(w)=0^{|w|}u$ for some word $u$.
+\end{proposition}
+\begin{proof}
+Write $\frac{n}{|w|}=c>1$. Thus, $f_1(w)=x$, $f_2(x)=0^{(c-1)|w|}x$ and $f_3(0^{(c-1)|w|}x)=0^{c-1|w|}x=f(w)$. Since $|x|=|w|$, $|f(w)|=n$ and hence, $f^*(w)=f(w)$. In addition, $(c-1)|w|\geq|w|$. 
+\end{proof}
+
+\begin{proposition}
+\label{1-back}
+If $|w|<n$ and $w=w'k$ where $0<k=max(w)$, then $b(w)=uw$ and $max(u)\leq max(w)$. 
+\end{proposition}
+\begin{proof}
+Write $w=w'k$. Thus, $b_1(w)=xk(w'k)^r$, $r>0$. $b_2(xk(w'k)^r)=y(w'k)^r$. $b_3(y(w'k)^r)=uw'k=uw$. It is easy to see that $\max{u}\leq k$.
+\end{proof}
+
+\begin{proposition}
+\label{*-back}
+If $w\in L_n$, $|w|^m=n$, $m>1$ and $w= 0^l\sigma\hat{w}$ such that $\sigma\neq 0$, then $b^*(w)=u\hat{w}w^{m-1}$ for some $u$. Note that in particular, $|b^*(w)|=n$.
+\end{proposition}
+
+\begin{proof}
+Since $w\in L_n$ and $w\neq 0$, $b_1(w)=w^m=(0^l\sigma w'k)^m$. 
+$$b(w)=b_3(b_2((0^l\sigma\hat{w})^m))=b_3((xk)(w'k)^{m-1})=y(w'k)^{m-1}=y\sigma-1\hat{w}w^{m-1}.$$
+Now, if $|y\sigma-1\hat{w}w^{m-1}=n$, then $y\sigma-1\hat{w}w^{m-1}=b^*(w)$ and we are done. Otherwise, 
+$$b^*(w^{m-1})=b^r(y\sigma-1\hat{w}w^{m-1}).$$
+Hence, the words $b(y\sigma-a\hat{w}w^{m-1}),b^2(y\sigma-\hat{w}w^{m-1}),\dots,b^{r-1}(y\sigma-1\hat{w}w^{m-1})$ are of length less than $n$.
+We apply Proposition \ref{1-back} on these words and we get that for each $l\leq r-1$,  $b^l(y\sigma-1\hat{w}w^{m-1})=u_1u_2\dots u_ly\sigma-1\hat{w}w^{m-1}$.
+\end{proof}
+
+\begin{proposition}
+Assume that $u\in \mathbb{N}^n$ corresponds to $w\in L_n$ such that $|w|<n$. then, $u$ is a subword of $w^\infty$. 
+\end{proposition}
+
+\begin{proof}
+If $u=0^n$, then $u$ is a prefix of $w^\infty$ and we are done.
+Otherwise, $w=0^l\sigma\hat{w}$ where $\sigma\neq 0$ and take $m$ such that $|w|^m=n$.
+Note that $m>1$.
+By Propositions \ref{newforward} and  \ref{*-back}, $b^*(w)wf^*(w)=x\hat{w}w^{m-1}w0^|w|y$ is a subword of $w^\infty$.
+Hence,
+$$\hat{w}(0^l\sigma\hat{w})^m0^l \text{ is a subword of } w^\infty.$$
+$u$ is a rotation of $w^m$ thus $u$ is a subword of $\hat{w}(0^l\sigma\hat{w})^m0^l$ which implies that $u$ is a subword of $w^\infty$.
+\end{proof}
+
+\begin{proposition}
+Assume that $u=yx\in\mathbb{N}^n$ corresponds to $w=xy\in L_n$ where $|w|=n$. If $x\neq 0^r$, then $u$ is a subword of $w^\infty$. 
+\end{proposition}
+
+\begin{proof}
+We show that $u=yx$ is a subword of $b^*(w)w$. Write $x=0^l\sigma z$ where $\sigma\neq 0$. Thus, since $|w|=n$, $b(w)=\sigma-1zy$. If $b(w)=b^*(w)$, then 
+$$b^*(w)w=v(\sigma-1)zyx$$
+and we get that $u$ is a subowrd of $b^*(w)b(w)$.
+Otherwise, $|(\sigma-1)zy|$ does not divides $n$, and in particular, $|\sigma-1zy|<n$.
+By applying Proposition \ref{1-back} several times, we get that $b*(w)=v(\sigma-1)zy$ for some $v$, and $u=yx$ is a subword of $b^*(w)w=v(\sigma-1)zyxy$.
+\end{proof}
+
 \end{document}

### 2016-11-03 infdebruijn.tex
aaa

@@
 \newtheorem{claim}[theorem]{Claim}
+\newtheorem{lemma}[theorem]{Lemma}
 
@@
 
+\begin{lemma}
+Assume that $w=0^lv\in L_n$ and $|w|=n$.
+Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
+Take $k\in \N$ such that $|z_1|\leq|(\sigma z_2)^k|$.
+Then, $z_1$ is a suffix of $(\sigma z_2)^k$.
+\end{lemma}
+
+\begin{proof}
+Assume for a contradiction that $z_1$ is not a suffix of $(\sigma z_1)^k$, and hence there are $\tau\neq \tau'$ in $\N$ and a word $y$, such that $\tau'y$ is a suffix of $\sigma z_2$, and 
+$$z_1=x\tau y(\sigma z_2)^r, \ (\sigma z_2)^k= x'\tau' y(\sigma z_2)^r.$$
+Clearly, $\tau<\tau'$ since otherwise, $\tau'<\tau$, and we get that 
+$w=0^lz_1\sigma z_2=0^lx\tau y (\sigma z_2)^{r+1}$. However, if we assume that $\tau'<\tau$, $w'=(\sigma z_2)^r0^lx\tau y$ is lexicographically larger than $w$, in contradiction to $w\in L_n$.
+\end{proof}
+
+\begin{corrolary}
+Assume that $w=0^lv\in L_n$ and $|w|=n$.
+Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
+Take $m\in \N$ and a suffix of $\sigma z_2$, $x$ such that $|x(\sigma z_2)^{m+1}|=n$.
+Then, $z_1$ is a suffix of $x(\sigma z_2)^m$.
+\end{corrolary}
+\begin{proof}
+ This is a consequence of the previous Lemma and the fact that $|0^lz_1|=|x(\sigma z_2)|^m$.
+\end{proof}
+
+\begin{proposition}
+Assume that $u=v0^l\in\mathbb{N}^n$ corresponds to $w=0^lv\in L_n$ where $|w|=n$. Then, $u$ is a subword of $w^\infty$. 
+\end{proposition}
+
+\begin{proof}
+Write $w=0^lz_1\sigma z_2$ where $\sigma\in \N$ is the first digit in $w$ so that  $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
+Note that such digit exists since the last digit in $w$ satisfies this requirement.
+
+Now, since $|0^{l+|z_1|}(\sigma+1)z_2|=n$ and $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations, $0^{l+|z_1|}(\sigma+1)z_2=(w')^m$ where $w'\in L_n$.
+Note that $0^{l+|z_1|}$ is a prefix of $w'$.
+We consider three possibilities
+
+\begin{description}
+
+\item{Case 1.}
+
+%$m=1$. Therefore, $|w'|=n$. In this case, $b(w')=\sigma z_2$. Since $l>0$, $|\sigma z_2|<n$. By applying Proposition \ref{1-back} several times, we get that $b^*{w'}=v'\sigma z_2$.
+
+\end{description}
+
+\end{proof}
+
 \end{document}

### 2016-11-05 infdebruijn.tex
aaa

@@
 \begin{lemma}
+\label{z1}
 Assume that $w=0^lv\in L_n$ and $|w|=n$.
@@
 \begin{corrolary}
+\label{z1-suffix}
 Assume that $w=0^lv\in L_n$ and $|w|=n$.
 Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Take $m\in \N$ and a suffix of $\sigma z_2$, $x$ such that $|x(\sigma z_2)^{m+1}|=n$.
-Then, $z_1$ is a suffix of $x(\sigma z_2)^m$.
+Then, there are words $x,y$ such that $z_2=xy$, $w=0^ly(\sigma xy)^{r+1}$ and $z_1=y(\sigma xy)^r$.
 \end{corrolary}
@@
 \begin{proposition}
-Assume that $u=v0^l\in\mathbb{N}^n$ corresponds to $w=0^lv\in L_n$ where $|w|=n$. Then, $u$ is a subword of $w^\infty$. 
+Assume that $v0^l\in\mathbb{N}^n$ corresponds to $w=0^lv\in L_n$ where $|w|=n$ and $l>0$. Then, $v0^l$ is a subword of $w^\infty$. 
 \end{proposition}
@@
 Write $w=0^lz_1\sigma z_2$ where $\sigma\in \N$ is the first digit in $w$ so that  $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Note that such digit exists since the last digit in $w$ satisfies this requirement.
+Note that such a digit exists since the last digit in $w$ satisfies this requirement.
+Hence, $v=z_1\sigma z_2$.
 
-Now, since $|0^{l+|z_1|}(\sigma+1)z_2|=n$ and $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations, $0^{l+|z_1|}(\sigma+1)z_2=(w')^m$ where $w'\in L_n$.
+By Corollary \ref{z1-suffix}, $z_2=xy$ and $z_1=y(\sigma xy)^r$.
+Now, since $|0^{l+|z_1|}(\sigma+1)z_2|=n$ and $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations, $0^{l+|z_1|}(\sigma+1)z_2=(w')^{k+1}$ where $w'\in L_n$.
 Note that $0^{l+|z_1|}$ is a prefix of $w'$.
@@
 
-\item{Case 1.}
+\item{Case 1.}  $\sigma z_2\in L_n$. We show that in this case, $v0^l$ is a subword of $b^*(b^*(w'))(b^*(w'))w'$, which is a subword of $w^\infty$.
 
-%$m=1$. Therefore, $|w'|=n$. In this case, $b(w')=\sigma z_2$. Since $l>0$, $|\sigma z_2|<n$. By applying Proposition \ref{1-back} several times, we get that $b^*{w'}=v'\sigma z_2$.
+$b_1(w')=w'^{k+1}=0^{l+|z_1|}(\sigma+1)z_2$.
+Hence, $b(w')=b_3(b_2(0^{l+|z_1|}(\sigma+1)z_1))=\sigma z_2$.
+Since $\sigma z_2\in L_n$, $b(w')=b^*(w')=\sigma z_2$ and in particular, $|(\sigma z_2)^{m+1}|=n$ for some $m\in \N$.
+Observe that $|z_1|\leq |\sigma z_2|^m$ and use Lemma \ref{z1} to conclude that $z_1$ is a suffix of $(\sigma z_2)^m$.
+
+By invoking Proposition \ref{1-back} several times, $b^*(\sigma z_2)= u(\sigma z_2)^m$ for some $u$. Hence, $v0^l=z_1\sigma z_2 0^l$ is a subword of 
+$$b^*(b^*(w'))b^*(w')b(w')=u(\sigma z_2)^{m+1}0^{l+|z_1|}x'.$$
+
+\item{Case 2.}
+
+Now, $b_1(\sigma z_2) = (\sigma z_2)^{m+1}$ and by Corollary \ref{z1-suffix}, $z_1$ is a suffix of $(\sigma z_2)^m$.
+Since the last digit in $(\sigma z_2)$ is not zero, by applying Proposition \ref{1-back} several times (possibly none), we get that $b^*{\sigma z_2}=x(\sigma z_2)^m$.
+As a result we have,
+$$b^*(b^*(w'))(b^*(w'))w'= x(\sigma z_2)^m (\sigma z_2) 0^{l+|z_1|}x'.$$
+Therefore, $v0^l=z_1\sigma z_2 0^l$ is a subword of  $b^*(b^*(w'))(b^*(w'))w'$ as required.
+
+\end{description}
+
+Before we deal with the other cases, we note that $b_1(\sigma z_2)=b_1(\sigma xy)=x'y(\sigma xy)^{r+1}$ for some $x'$ that satisfies $|x'|=l>0$.
+
+\begin{description}
+\item{Case 2.} $\sigma z_2\notin L_n$  and $x'\neq 0^l$. We show that in this case, $v0^l$ is a subword of $b^*(w')w'$, which is a subword of $w^\infty$.
+
+Recall that $b(w')=\sigma z_2$ which is, by assumption, not a key-word.
+Since $x'\neq 0^l$, several invocations of Proposition \ref{1-back} imply that $b^*(\sigma z_2)=x''y(\sigma z_2)^{r+1}$.
+Since $v=z_1\sigma z_2=y(\sigma z_2)^{r+1}$, we get that $v0^l$ is a subword of
+$$b^*(w')w'=x''y(\sigma z_2)^{r+1}0^{l+|z_1}u.$$
+
+\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$.
+In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$.
+Write $w''=(\sigma xy)^{r+1}0^ly$ (is it a key-word?).
+Then, $v0^l$ is a subword of $b^*(w'')w''$ (really?).
 

### 2016-11-05 infdebruijn.tex
aaa

@@
 
+\begin{lemma}
+Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w$ is not a key-word. 
+\end{lemma}
+
+\begin{proof}
+Assume for a contradiction that $w$ is a key-word of length $n$, and take a maximal $t\in \N$ such that $x0^ly=x'(0^ly)^{t+1}$.
+First, we note that $x'\neq \varepsilon$.
+Indeed, if $x'=\varepsilon$, then $w=(0^ly)(0^ly)^{t(r+1)}$, a periodic word, and $w$ then is not an key-word.
+
+Now we claim that $|x'|<|y|$.
+\end{proof}
+
 \begin{proposition}
@@
 
-\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$.
-In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$.
-Write $w''=(\sigma xy)^{r+1}0^ly$ (is it a key-word?).
-Then, $v0^l$ is a subword of $b^*(w'')w''$ (really?).
+\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$. In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$. Note that $w=0^ly(x''0^ly)^{r+1}$ and use Lemma \ref{} to achieve a contradiction.
 

### 2016-11-05 infdebruijn.tex
I think I got it now. I intend to check the proofs again, it is better if you will do it also

@@
 \begin{lemma}
+If $uv=vu$ and $u,v\neq\varepsilon$, then there is some word $w$, such that $u,v\in\{w\}^*$.
+\end{lemma}
+
+\begin{proof}
+By induction on $|u|+|v|$.
+If $|u|=|v|$, $u=v$ and we are done.
+Otherwise, assume w.l.o.g.
+that $|u|>|v|$ and write $u=vx$ (since $uv=vu$).
+Then, $ux=vxv=vvx=vu$.
+We see that $xv=vx$.
+By the induction hypothesis, $x=w^k$ and $v=w^l$.
+Hence, $u=w^{l+k}$ as required.
+\end{proof}
+
+\begin{lemma}
 Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w$ is not a key-word. 
@@
 
-Now we claim that $|x'|<|y|$.
+Now we claim that $|x'|<|0^ly|$.
+For verifying this claim, assume that $|x|\geq |0^ly|$ and write $x=x'_1x'_2$, where $|x'_2|=|0^ly|$.
+By maximality of $t$, $x'_2\neq 0^ly$, and since $w\in L_n$, $x'_2<_{lex} ^ly$.
+Therefore, $(x0^ly)^rx_1'x_2'(0^ly)^{t+1}0^ly$, is a rotation of $w$ which is lexicographically larger then $w$, in contradiction to $w\in L_n$.
+
+To summary our conclusions, we have $w=0^ly(x0^ly)^rx'(0^ly)^{t+1}\in L_n$, and $|x'|<|0^ly|$.
+Write $0^ly=z_1z_2$ where $|x'|=|z_2|$.
+Therefore, $w=z_1z_2(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+1})$.
+We look at the rotation of $w$, $w'=(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+2})$.
+Since $w\in L_n$, $w$ is lexicographically larger than $w'$ and in particular,
+$(z_1z_2z_2(z_1z_2)^{t+1})\geq_{lex}(z_2(z_1z_2)^{t+2})$ which implies that
+$$z_1z_2z_2\geq_{lex}z_2z_1z_2.$$
+In addition, $z_2z_1z_2$ is a suffix of $w$ while $z_1z_2z_2$ is a subword of $w$. Hence, as $w\in L_n$ we have,
+$$z_2z_1z_2\geq z_1z_2z_2.$$
+As a result, $z_2z_1z_2=z_1z_2z_2$ thus $z_2z_1=z_1z_2$. By Lemma \ref{}, $z_1=z^{l_1}$ and $z_2=z^{l_2}$ for some non empty word $z$. Therefore, $w=z^m$ for some $z>0$ in contradiction to $w\in L_n$.
+
 \end{proof}
@@
 
-\item{Case 2.}
-
-Now, $b_1(\sigma z_2) = (\sigma z_2)^{m+1}$ and by Corollary \ref{z1-suffix}, $z_1$ is a suffix of $(\sigma z_2)^m$.
-Since the last digit in $(\sigma z_2)$ is not zero, by applying Proposition \ref{1-back} several times (possibly none), we get that $b^*{\sigma z_2}=x(\sigma z_2)^m$.
-As a result we have,
-$$b^*(b^*(w'))(b^*(w'))w'= x(\sigma z_2)^m (\sigma z_2) 0^{l+|z_1|}x'.$$
-Therefore, $v0^l=z_1\sigma z_2 0^l$ is a subword of  $b^*(b^*(w'))(b^*(w'))w'$ as required.
-
 \end{description}
@@
 
+\begin{theorem}
+$w^\infty$ is an infinite De-Bruijn sequence.
+\end{theorem}
+
+\begin{proof}
+According to Propositions \ref{}, every $n$-sequence is a subword of $w^\infty$. By the ``onion theorem" and by the pigeonhole principle, every $n$-sequence appears only once at $w^\infty$.
+\end{proof}
+
 \end{document}

### 2016-11-07 infdebruijn.tex
aa

@@
 \begin{definition}
-A word $u\in \mathbb{N}$ corresponds to $w\in L_n$ if $u$ is a rotation of $w^{\frac{n}{|w|}}$. Note that each $u\in \mathbb{N}$ corresponds to exactly one word $w\in L_n$.
+A word $u\in \mathbb{N}^n$ corresponds to $w\in L_n$ if $u$ is a rotation of $w^{\frac{n}{|w|}}$. Note that each $u\in \mathbb{N}^n$ corresponds to exactly one word $w\in L_n$.
 \end{definition}
@@
 \label{newforward}
-If $w\in L_n$ and $|w|<n$, then $f^*(w)=f(w)=0^{|w|}u$ for some word $u$.
+If $w\in L_n$ and $|w|<n$, then $f^*(w)=f(w)=0^{n-|w|}x$ for some word $x$.
 \end{proposition}
 \begin{proof}
-Write $\frac{n}{|w|}=c>1$. Thus, $f_1(w)=x$, $f_2(x)=0^{(c-1)|w|}x$ and $f_3(0^{(c-1)|w|}x)=0^{c-1|w|}x=f(w)$. Since $|x|=|w|$, $|f(w)|=n$ and hence, $f^*(w)=f(w)$. In addition, $(c-1)|w|\geq|w|$. 
+Write $f_1(w)=x$, $f_2(x)=0^{n-|w|}x$.
+Since $w\in L_n$ and $|w|<n$, $n-|w|\geq \frac{n}{2}$.
+Moreover, the last digit in $x$ is not zero.
+Hecne, $f(w)=f_3(0^{n-|w|}x)=0^{n-|w|}x$.
+Since $|0^{n-|w|}x|=n$, we have $f(w)=f^*(w)=0^{n-|w|}x$.
 \end{proof}
@@
 \label{1-back}
-If $|w|<n$ and $w=w'k$ where $0<k=max(w)$, then $b(w)=uw$ and $max(u)\leq max(w)$. 
+Take $|w|<n$ so that $w=w'k$ where $0<k=max(w)$, then $b(w)=uw$ and $max(u)\leq max(w)$. 
 \end{proposition}
@@
 
+%\begin{proposition}
+%Take $|w|<n$ so that $w=w'k$ where $0<k=max(w)$. Write $b_1(w)=xw^m$ where $x$ is a non-empty suffix of $w$ (possibly $x=w$). Then, $b(w)=uw^m$ and $max(u)\leq max(w)$. 
+%\end{proposition}
+
+%\begin{proof}
+%Note that $b(w)=b_3(b_2(xw^m))=yw^m$.
+This holds since the last digit in $x$ is $k>0$.
+Clearly, $max(y)\leq max(w)$.
+If $|yw^m|=n$, then $b^*(w)=b(w)$ and we are done with $u=y$.
+Otherwise, apply the previous Proposition several times.
+%\end{proof}
+
 \begin{proposition}
 \label{*-back}
-If $w\in L_n$, $|w|^m=n$, $m>1$ and $w= 0^l\sigma\hat{w}$ such that $\sigma\neq 0$, then $b^*(w)=u\hat{w}w^{m-1}$ for some $u$. Note that in particular, $|b^*(w)|=n$.
+If $w\in L_n$, $|w|^m=n$, $m>1$ and $w= 0^l\sigma\hat{w}$ such that $\sigma\neq 0$, then $b^*(w)=u\hat{w}w^{m-1}$ for some $u$.
 \end{proposition}
@@
 \begin{proof}
-Since $w\in L_n$ and $w\neq 0$, $b_1(w)=w^m=(0^l\sigma w'k)^m$. 
-$$b(w)=b_3(b_2((0^l\sigma\hat{w})^m))=b_3((xk)(w'k)^{m-1})=y(w'k)^{m-1}=y\sigma-1\hat{w}w^{m-1}.$$
-Now, if $|y\sigma-1\hat{w}w^{m-1}=n$, then $y\sigma-1\hat{w}w^{m-1}=b^*(w)$ and we are done. Otherwise, 
-$$b^*(w^{m-1})=b^r(y\sigma-1\hat{w}w^{m-1}).$$
-Hence, the words $b(y\sigma-a\hat{w}w^{m-1}),b^2(y\sigma-\hat{w}w^{m-1}),\dots,b^{r-1}(y\sigma-1\hat{w}w^{m-1})$ are of length less than $n$.
-We apply Proposition \ref{1-back} on these words and we get that for each $l\leq r-1$,  $b^l(y\sigma-1\hat{w}w^{m-1})=u_1u_2\dots u_ly\sigma-1\hat{w}w^{m-1}$.
+Since $w\in L_n$ and $w\neq 0$, $b(w)$ is defined and 
+$$b(w)=(\sigma-1)\hat{w}w^{m-1}.$$
+If $b(w)\in L_n$ we are done, and otherwise $|b(w)|<n$ and several invocations of the previous proposition provide the required.
 \end{proof}
@@
 If $u=0^n$, then $u$ is a prefix of $w^\infty$ and we are done.
-Otherwise, $w=0^l\sigma\hat{w}$ where $\sigma\neq 0$ and take $m$ such that $|w|^m=n$.
+Otherwise, $w=0^l\sigma\hat{w}$ where $\sigma\neq 0$.
+Take $m$ such that $|w|^m=n$.
 Note that $m>1$.
-By Propositions \ref{newforward} and  \ref{*-back}, $b^*(w)wf^*(w)=x\hat{w}w^{m-1}w0^|w|y$ is a subword of $w^\infty$.
+By Propositions \ref{newforward} and  \ref{*-back}, $b^*(w)wf^*(w)=x\hat{w}w^{m-1}w0^{|w|}y$, which is also a subword of $w^\infty$.
 Hence,
@@
 \begin{proof}
-We show that $u=yx$ is a subword of $b^*(w)w$. Write $x=0^l\sigma z$ where $\sigma\neq 0$. Thus, since $|w|=n$, $b(w)=\sigma-1zy$. If $b(w)=b^*(w)$, then 
-$$b^*(w)w=v(\sigma-1)zyx$$
+We show that $u=yx$ is a subword of $b^*(w)w$. Write $x=0^l\sigma z$ where $\sigma\neq 0$. Thus, since $|w|=n$, $b(w)=(\sigma-1)zy$. If $b(w)=b^*(w)$, then 
+$$b^*(w)w=(\sigma-1)zyx$$
 and we get that $u$ is a subowrd of $b^*(w)b(w)$.
-Otherwise, $|(\sigma-1)zy|$ does not divides $n$, and in particular, $|\sigma-1zy|<n$.
-By applying Proposition \ref{1-back} several times, we get that $b*(w)=v(\sigma-1)zy$ for some $v$, and $u=yx$ is a subword of $b^*(w)w=v(\sigma-1)zyxy$.
+Otherwise, $|(\sigma-1)zy|$ does not divides $n$, and in particular, $|(\sigma-1)zy|<n$.
+By applying Proposition \ref{1-back} several times, we get that $b^*(w)=v(\sigma-1)zy$ for some $v$, and $u=yx$ is a subword of $b^*(w)w=v(\sigma-1)zyxyx$.
 \end{proof}
@@
 Assume that $w=0^lv\in L_n$ and $|w|=n$.
-Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Take $k\in \N$ such that $|z_1|\leq|(\sigma z_2)^k|$.
-Then, $z_1$ is a suffix of $(\sigma z_2)^k$.
+Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in $v$ such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
+Take $k\in \N$ and a suffix of $(\sigma z_2)$, $u$ such that $|u(\sigma z_2)^{k+1}|=|z_1(\sigma z_2)|$.
+Then, $u(\sigma z_2)^{k+1}= z_1(\sigma z_2)$.
 \end{lemma}
@@
 \begin{proof}
-Assume for a contradiction that $z_1$ is not a suffix of $(\sigma z_1)^k$, and hence there are $\tau\neq \tau'$ in $\N$ and a word $y$, such that $\tau'y$ is a suffix of $\sigma z_2$, and 
+Assume for a contradiction that the claim is false, and hence $z_1\neq u(\sigma z_2)^k$.
+Therefore, there are $\tau\neq \tau'$ in $\N$ and a word $y$, such that $\tau'y$ is a suffix of $\sigma z_2$, and
 $$z_1=x\tau y(\sigma z_2)^r, \ (\sigma z_2)^k= x'\tau' y(\sigma z_2)^r.$$
@@
 \begin{lemma}
+\label{concatenation}
 If $uv=vu$ and $u,v\neq\varepsilon$, then there is some word $w$, such that $u,v\in\{w\}^*$.
@@
 \begin{lemma}
-Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w$ is not a key-word. 
+\label{not-in-Ln}
+Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w\notin L_n$.
 \end{lemma}
@@
 First, we note that $x'\neq \varepsilon$.
-Indeed, if $x'=\varepsilon$, then $w=(0^ly)(0^ly)^{t(r+1)}$, a periodic word, and $w$ then is not an key-word.
+Indeed, if $x'=\varepsilon$, then $w=(0^ly)(0^ly)^{(t+1)(r+1)}$, a periodic word, and then $w\notin L_n$.
 
 Now we claim that $|x'|<|0^ly|$.
-For verifying this claim, assume that $|x|\geq |0^ly|$ and write $x=x'_1x'_2$, where $|x'_2|=|0^ly|$.
-By maximality of $t$, $x'_2\neq 0^ly$, and since $w\in L_n$, $x'_2<_{lex} ^ly$.
-Therefore, $(x0^ly)^rx_1'x_2'(0^ly)^{t+1}0^ly$, is a rotation of $w$ which is lexicographically larger then $w$, in contradiction to $w\in L_n$.
+For verifying this claim, assume that $|x'|\geq |0^ly|$ and write $x'=x'_1x'_2$, where $|x'_2|=|0^ly|$.
+By maximality of $t$, $x'_2\neq 0^ly$, and since $w\in L_n$, $x'_2<_{lex} 0^ly$.
+Therefore, $$w'=(x0^ly)^rx_1'x_2'(0^ly)^{t+1}0^ly$$ is a rotation of $w$ which is lexicographically larger then $w$, in contradiction to $w\in L_n$.
 
-To summary our conclusions, we have $w=0^ly(x0^ly)^rx'(0^ly)^{t+1}\in L_n$, and $|x'|<|0^ly|$.
+To summary our conclusions, we have $w=0^ly(x'(0^ly)^{t+1})^{r+1}\in L_n$, and $|x'|<|0^ly|$.
 Write $0^ly=z_1z_2$ where $|x'|=|z_2|$.
-Therefore, $w=z_1z_2(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+1})$.
-We look at the rotation of $w$, $w'=(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+2})$.
-Since $w\in L_n$, $w$ is lexicographically larger than $w'$ and in particular,
+Therefore, $$w=z_1z_2(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+1}).$$
+
+We look now at ù rotation of $w$, $w'=(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+2})$. Since $w\in L_n$, $w$ is lexicographically larger than $w'$ and in particular,
 $(z_1z_2z_2(z_1z_2)^{t+1})\geq_{lex}(z_2(z_1z_2)^{t+2})$ which implies that
-$$z_1z_2z_2\geq_{lex}z_2z_1z_2.$$
-In addition, $z_2z_1z_2$ is a suffix of $w$ while $z_1z_2z_2$ is a subword of $w$. Hence, as $w\in L_n$ we have,
-$$z_2z_1z_2\geq z_1z_2z_2.$$
-As a result, $z_2z_1z_2=z_1z_2z_2$ thus $z_2z_1=z_1z_2$. By Lemma \ref{}, $z_1=z^{l_1}$ and $z_2=z^{l_2}$ for some non empty word $z$. Therefore, $w=z^m$ for some $z>0$ in contradiction to $w\in L_n$.
+$z_1z_2z_2\geq_{lex}z_2z_1z_2$, and hence
+$$z_1z_2\geq_{lex}z_2z_1.$$
+In addition, $z_2z_1z_2$ is a suffix of $w$ while $z_1z_2z_2$ is a subword of $w$. Hence, as $w\in L_n$ we have, $z_2z_1z_2\geq_{lex} z_1z_2z_2$, and hence
+$$z_2z_1\geq_{lex}z_1z_2.$$
+As a result, $z_2z_1=z_1z_2$m and then by Lemma \ref{concatenation}, $z_1=z^{l_1}$ and $z_2=z^{l_2}$ for some non empty word $z$. Therefore, $w=z^m$ for some $z>0$ in contradiction to $w\in L_n$.
 
@@
 Since $v=z_1\sigma z_2=y(\sigma z_2)^{r+1}$, we get that $v0^l$ is a subword of
-$$b^*(w')w'=x''y(\sigma z_2)^{r+1}0^{l+|z_1}u.$$
+$$b^*(w')w'=x''y(\sigma z_2)^{r+1}0^{l+|z_1|}u.$$
 
-\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$. In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$. Note that $w=0^ly(x''0^ly)^{r+1}$ and use Lemma \ref{} to achieve a contradiction.
+\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$.
+In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$.
+Note that $w=0^ly(x''0^ly)^{r+1}$ and use Lemma \ref{not-in-Ln} to obtain a contradiction.
 

### 2016-11-10 infdebruijn.tex
.

--- 2016-11-05 infdebruijn.tex
@@
 \newtheorem{claim}[theorem]{Claim}
-\newtheorem{lemma}[theorem]{Lemma}
 
@@
 \begin{proposition}
-For a word $w=w(i)$ be the $i$th word in the above enumeration.
-Let $l$ be the number of leading zeros in $w$ and let $\hat{w}=\rl{b_1(b^*(w))}{l}$.
-Then, inserting the cycle $\T{\rl{b_1(w)}{s}}_{s=0}^{n-1}$ after the word $\hat{w}_{1..(n-l)}0^l$ in $\T{u(j)}_{j=0}^{i-1}$ yields the sequence $\T{u(j)}_{j=0}^{i}$.
+	Let $w=w(i)$ for some $i$ and let $l$ be the number of leading zeros in $w$.
+	Then, inserting the cycle $\T{R^{-l-n-1}(w),\dots,R^{-l}(w)}$ to $\T{u(j)}_{j=0}^{i-1}$
+	 after the word obtained from $R^{-l}(w)$ by decreasing its first letter by one
+	 yields the sequence $\T{u(j)}_{j=0}^{i}$.
 \end{proposition}
 
-\section{Where can I find $w$ as a sub-word of $w^\infty$? (second try...)}
-
-\begin{definition}
-For a word $w$, $max(w)$ is the maximal digit in $w$.
-\end{definition}
-
-\begin{definition}
-A word $u\in \mathbb{N}$ corresponds to $w\in L_n$ if $u$ is a rotation of $w^{\frac{n}{|w|}}$. Note that each $u\in \mathbb{N}$ corresponds to exactly one word $w\in L_n$.
-\end{definition}
-
-\begin{proposition}
-\label{newforward}
-If $w\in L_n$ and $|w|<n$, then $f^*(w)=f(w)=0^{|w|}u$ for some word $u$.
-\end{proposition}
-\begin{proof}
-Write $\frac{n}{|w|}=c>1$. Thus, $f_1(w)=x$, $f_2(x)=0^{(c-1)|w|}x$ and $f_3(0^{(c-1)|w|}x)=0^{c-1|w|}x=f(w)$. Since $|x|=|w|$, $|f(w)|=n$ and hence, $f^*(w)=f(w)$. In addition, $(c-1)|w|\geq|w|$. 
-\end{proof}
-
-\begin{proposition}
-\label{1-back}
-If $|w|<n$ and $w=w'k$ where $0<k=max(w)$, then $b(w)=uw$ and $max(u)\leq max(w)$. 
-\end{proposition}
-\begin{proof}
-Write $w=w'k$. Thus, $b_1(w)=xk(w'k)^r$, $r>0$. $b_2(xk(w'k)^r)=y(w'k)^r$. $b_3(y(w'k)^r)=uw'k=uw$. It is easy to see that $\max{u}\leq k$.
-\end{proof}
-
-\begin{proposition}
-\label{*-back}
-If $w\in L_n$, $|w|^m=n$, $m>1$ and $w= 0^l\sigma\hat{w}$ such that $\sigma\neq 0$, then $b^*(w)=u\hat{w}w^{m-1}$ for some $u$. Note that in particular, $|b^*(w)|=n$.
-\end{proposition}
-
-\begin{proof}
-Since $w\in L_n$ and $w\neq 0$, $b_1(w)=w^m=(0^l\sigma w'k)^m$. 
-$$b(w)=b_3(b_2((0^l\sigma\hat{w})^m))=b_3((xk)(w'k)^{m-1})=y(w'k)^{m-1}=y\sigma-1\hat{w}w^{m-1}.$$
-Now, if $|y\sigma-1\hat{w}w^{m-1}=n$, then $y\sigma-1\hat{w}w^{m-1}=b^*(w)$ and we are done. Otherwise, 
-$$b^*(w^{m-1})=b^r(y\sigma-1\hat{w}w^{m-1}).$$
-Hence, the words $b(y\sigma-a\hat{w}w^{m-1}),b^2(y\sigma-\hat{w}w^{m-1}),\dots,b^{r-1}(y\sigma-1\hat{w}w^{m-1})$ are of length less than $n$.
-We apply Proposition \ref{1-back} on these words and we get that for each $l\leq r-1$,  $b^l(y\sigma-1\hat{w}w^{m-1})=u_1u_2\dots u_ly\sigma-1\hat{w}w^{m-1}$.
-\end{proof}
-
-\begin{proposition}
-Assume that $u\in \mathbb{N}^n$ corresponds to $w\in L_n$ such that $|w|<n$. then, $u$ is a subword of $w^\infty$. 
-\end{proposition}
-
-\begin{proof}
-If $u=0^n$, then $u$ is a prefix of $w^\infty$ and we are done.
-Otherwise, $w=0^l\sigma\hat{w}$ where $\sigma\neq 0$ and take $m$ such that $|w|^m=n$.
-Note that $m>1$.
-By Propositions \ref{newforward} and  \ref{*-back}, $b^*(w)wf^*(w)=x\hat{w}w^{m-1}w0^|w|y$ is a subword of $w^\infty$.
-Hence,
-$$\hat{w}(0^l\sigma\hat{w})^m0^l \text{ is a subword of } w^\infty.$$
-$u$ is a rotation of $w^m$ thus $u$ is a subword of $\hat{w}(0^l\sigma\hat{w})^m0^l$ which implies that $u$ is a subword of $w^\infty$.
-\end{proof}
-
-\begin{proposition}
-Assume that $u=yx\in\mathbb{N}^n$ corresponds to $w=xy\in L_n$ where $|w|=n$. If $x\neq 0^r$, then $u$ is a subword of $w^\infty$. 
-\end{proposition}
-
-\begin{proof}
-We show that $u=yx$ is a subword of $b^*(w)w$. Write $x=0^l\sigma z$ where $\sigma\neq 0$. Thus, since $|w|=n$, $b(w)=\sigma-1zy$. If $b(w)=b^*(w)$, then 
-$$b^*(w)w=v(\sigma-1)zyx$$
-and we get that $u$ is a subowrd of $b^*(w)b(w)$.
-Otherwise, $|(\sigma-1)zy|$ does not divides $n$, and in particular, $|\sigma-1zy|<n$.
-By applying Proposition \ref{1-back} several times, we get that $b*(w)=v(\sigma-1)zy$ for some $v$, and $u=yx$ is a subword of $b^*(w)w=v(\sigma-1)zyxy$.
-\end{proof}
-
-\begin{lemma}
-\label{z1}
-Assume that $w=0^lv\in L_n$ and $|w|=n$.
-Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Take $k\in \N$ such that $|z_1|\leq|(\sigma z_2)^k|$.
-Then, $z_1$ is a suffix of $(\sigma z_2)^k$.
-\end{lemma}
-
-\begin{proof}
-Assume for a contradiction that $z_1$ is not a suffix of $(\sigma z_1)^k$, and hence there are $\tau\neq \tau'$ in $\N$ and a word $y$, such that $\tau'y$ is a suffix of $\sigma z_2$, and 
-$$z_1=x\tau y(\sigma z_2)^r, \ (\sigma z_2)^k= x'\tau' y(\sigma z_2)^r.$$
-Clearly, $\tau<\tau'$ since otherwise, $\tau'<\tau$, and we get that 
-$w=0^lz_1\sigma z_2=0^lx\tau y (\sigma z_2)^{r+1}$. However, if we assume that $\tau'<\tau$, $w'=(\sigma z_2)^r0^lx\tau y$ is lexicographically larger than $w$, in contradiction to $w\in L_n$.
-\end{proof}
-
-\begin{corrolary}
-\label{z1-suffix}
-Assume that $w=0^lv\in L_n$ and $|w|=n$.
-Write $w=0^lz_1\sigma z_2$ where $\sigma$ is the first digit in such that $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Then, there are words $x,y$ such that $z_2=xy$, $w=0^ly(\sigma xy)^{r+1}$ and $z_1=y(\sigma xy)^r$.
-\end{corrolary}
-\begin{proof}
- This is a consequence of the previous Lemma and the fact that $|0^lz_1|=|x(\sigma z_2)|^m$.
-\end{proof}
-
-\begin{lemma}
-Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w$ is not a key-word. 
-\end{lemma}
-
-\begin{proof}
-Assume for a contradiction that $w$ is a key-word of length $n$, and take a maximal $t\in \N$ such that $x0^ly=x'(0^ly)^{t+1}$.
-First, we note that $x'\neq \varepsilon$.
-Indeed, if $x'=\varepsilon$, then $w=(0^ly)(0^ly)^{t(r+1)}$, a periodic word, and $w$ then is not an key-word.
-
-Now we claim that $|x'|<|y|$.
-\end{proof}
-
-\begin{proposition}
-Assume that $v0^l\in\mathbb{N}^n$ corresponds to $w=0^lv\in L_n$ where $|w|=n$ and $l>0$. Then, $v0^l$ is a subword of $w^\infty$. 
-\end{proposition}
-
-\begin{proof}
-Write $w=0^lz_1\sigma z_2$ where $\sigma\in \N$ is the first digit in $w$ so that  $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations.
-Note that such a digit exists since the last digit in $w$ satisfies this requirement.
-Hence, $v=z_1\sigma z_2$.
-
-By Corollary \ref{z1-suffix}, $z_2=xy$ and $z_1=y(\sigma xy)^r$.
-Now, since $|0^{l+|z_1|}(\sigma+1)z_2|=n$ and $0^{l+|z_1|}(\sigma+1)z_2$ is lexicographically maximal among its rotations, $0^{l+|z_1|}(\sigma+1)z_2=(w')^{k+1}$ where $w'\in L_n$.
-Note that $0^{l+|z_1|}$ is a prefix of $w'$.
-We consider three possibilities
-
-\begin{description}
-
-\item{Case 1.}  $\sigma z_2\in L_n$. We show that in this case, $v0^l$ is a subword of $b^*(b^*(w'))(b^*(w'))w'$, which is a subword of $w^\infty$.
-
-$b_1(w')=w'^{k+1}=0^{l+|z_1|}(\sigma+1)z_2$.
-Hence, $b(w')=b_3(b_2(0^{l+|z_1|}(\sigma+1)z_1))=\sigma z_2$.
-Since $\sigma z_2\in L_n$, $b(w')=b^*(w')=\sigma z_2$ and in particular, $|(\sigma z_2)^{m+1}|=n$ for some $m\in \N$.
-Observe that $|z_1|\leq |\sigma z_2|^m$ and use Lemma \ref{z1} to conclude that $z_1$ is a suffix of $(\sigma z_2)^m$.
-
-By invoking Proposition \ref{1-back} several times, $b^*(\sigma z_2)= u(\sigma z_2)^m$ for some $u$. Hence, $v0^l=z_1\sigma z_2 0^l$ is a subword of 
-$$b^*(b^*(w'))b^*(w')b(w')=u(\sigma z_2)^{m+1}0^{l+|z_1|}x'.$$
-
-\item{Case 2.}
-
-Now, $b_1(\sigma z_2) = (\sigma z_2)^{m+1}$ and by Corollary \ref{z1-suffix}, $z_1$ is a suffix of $(\sigma z_2)^m$.
-Since the last digit in $(\sigma z_2)$ is not zero, by applying Proposition \ref{1-back} several times (possibly none), we get that $b^*{\sigma z_2}=x(\sigma z_2)^m$.
-As a result we have,
-$$b^*(b^*(w'))(b^*(w'))w'= x(\sigma z_2)^m (\sigma z_2) 0^{l+|z_1|}x'.$$
-Therefore, $v0^l=z_1\sigma z_2 0^l$ is a subword of  $b^*(b^*(w'))(b^*(w'))w'$ as required.
-
-\end{description}
-
-Before we deal with the other cases, we note that $b_1(\sigma z_2)=b_1(\sigma xy)=x'y(\sigma xy)^{r+1}$ for some $x'$ that satisfies $|x'|=l>0$.
-
-\begin{description}
-\item{Case 2.} $\sigma z_2\notin L_n$  and $x'\neq 0^l$. We show that in this case, $v0^l$ is a subword of $b^*(w')w'$, which is a subword of $w^\infty$.
-
-Recall that $b(w')=\sigma z_2$ which is, by assumption, not a key-word.
-Since $x'\neq 0^l$, several invocations of Proposition \ref{1-back} imply that $b^*(\sigma z_2)=x''y(\sigma z_2)^{r+1}$.
-Since $v=z_1\sigma z_2=y(\sigma z_2)^{r+1}$, we get that $v0^l$ is a subword of
-$$b^*(w')w'=x''y(\sigma z_2)^{r+1}0^{l+|z_1}u.$$
-
-\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$. In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$. Note that $w=0^ly(x''0^ly)^{r+1}$ and use Lemma \ref{} to achieve a contradiction.
-
-\end{description}
-
-\end{proof}
-
 \end{document}

### 2016-11-29 infdebruijn.tex
Cycle joining section

--- 2016-11-07 infdebruijn.tex
@@
 %\usepackage{balance}
+\usepackage{scrextend}
+\addtokomafont{labelinglabel}{\sffamily}
 
@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}     
+\newtheorem{definition}[theorem]{Definition}     
 \newtheorem{conjecture}[theorem]{Conjecture}
@@
 
+%\newcommand{\RotateLeft}{rlft}
+\DeclareMathOperator{\RotateLeft}{RotLft}
+
 %------------------------------------------- preamble ---------------------------
@@
 \newcommand{\N}{{\mathbb{N}}}
-\newcommand{\C}{{\mathbb{C}}}
 \newcommand{\Z}{{\mathbb{Z}}}
@@
 
-\title{On Combinatorial Games and de Bruijn Sequences}
+\title{An Infinite de Bruijn Sequence}
 
-\author{Yotam Svoray and %Gera Weiss\\
-Department of Computer Science \\
-Ben Gurion University of the Negev\\
-Israel
-}
+\author{}
 
@@
 \begin{document}
+\maketitle
+
+\section{A cycle joining Construction}
+
+\begin{definition}
+	A word in $\N^*$ is called a \emph{key word} if it is bigger in right-to-left lexicographical order than all of its rotations.
+\end{definition}
+
+\begin{definition}[Cycle Construction]
+For $n\in \N$, let $k_1,k_2,\dots$ be an enumeration in right-to-left lexicographic order of all the key words of length $n$ and let $z(k_i)$ be the number of leading zeros in $k_i$.
+Define $C_0=\T{0^n}$ and, for $i>0$, let $C_i$ be the sequence obtained from $C_{i-1}$ by adding
+	$$\T{\RotateLeft(k_i,z(k_i)+1),\RotateLeft(k_i,z(k_i)+2),\dots,\RotateLeft(k_i,z(k_i))}$$ 
+after the word $(\sigma-1)w$ where $\sigma w=\RotateLeft(k_i,z(k_i))$.
+\footnote{This is always possible because  $(\sigma-1)w$ is a rotation of a key word that is smaller than $k_i$ in left-to-right lexicographic order, i.e., it came earlier in the enumeration.}
+\end{definition}
+
+\begin{proposition}
+For every $l>0$ there is some $i>0$ such that the first $l$ words in $C_i$ are also the first $l$ words in $C_j$ for any $j>i$.
+\end{proposition}
+
+\begin{definition}
+Let $C_\infty$ be the infinite sequence whose prefixes are all prefixes of an infinite number of elements in $\{C_0,C_1,\dots\}$.
+\end{definition}
+
+\begin{proposition}
+The sequence $C_\infty$ is a de Bruijn sequence of order $n$, i.e., it is a Hamiltonian path over the infinite de Bruijn graph of order $n$ whose vertexes are the words $\N^n$ and whose edges are $\{ \T{ \sigma w, w \sigma'} \colon \sigma, \sigma' \in \N, w \in \N^{n-1} \}$.
+\end{proposition}
+
+\begin{definition}[Last on Necklace]
+Let $last(w)$ be true if and only if $w=\RotateLeft(k_i,z(k_i))$ for some $i$. i.e., if $w$ is the last member of its necklace (set of rotations) in the sequence. 
+\end{definition}
+
+\begin{definition}
+Let $nxt\colon \N^n \to \N^n$ be defined by
+$$nxt(\sigma w)=\begin{cases} 
+w(\sigma+1) & \text{if }last((\sigma+1)w) \\
+w0          & \text{if }last(\sigma w) \\
+w\sigma     & \text{otherwise} 
+\end{cases}$$
+\end{definition}
+
+\begin{proposition}
+For every $w\in \N^n$, $nxt(w)$ is the word that follows $w$ in the sequence $C_\infty$.
+\end{proposition}
+
+\begin{definition}
+Let $prv\colon \N^n \to \N^n$ be defined by
+$$prv(w\sigma)=\begin{cases} 
+(\sigma-1)w & \text{if }last(\sigma w) \\
+\sigma'w   & \text{if $\sigma =0$  and $\sigma'$ is the maximal such that $last(\sigma' w)$} \\
+\sigma w     & \text{otherwise} 
+\end{cases}$$
+\end{definition}
+
+\begin{proposition}
+For every $w\in \N^n\setminus \{0^n\}$, $prv(w)$ is the word that precedes $w$ in the sequence $C_\infty$.
+\end{proposition}
+
+\begin{proposition}
+Both $prv$ and $nxt$ can be computed in $O(n^2)$ time and space.
+\end{proposition}
+
+\begin{proposition}[Prefer Maximum]
+For every $\sigma \in \N$ and $w \in \N^{n-1}$, the word $\sigma w$ comes before the word $(\sigma+1) w$ in $C_\infty$.
+\end{proposition}
+\begin{proof}
+Let $k$ be a key word  of the form $0^z(k)\hat{w}$. We will prove the proposition for every rotation of $k$:
+
+\begin{description} 
+\item [First Case:] If $w=0^{z_1}\hat{w}0^{z_2}$ such that $z_1+z_2=z(k)$ and $z_1 \neq 0$ then we have that $w$ precedes  $w_1=0^{z_1-1}\hat{w}0^{z_2}1$ by the definition of $nxt$ and that $w_1$ precedes $1 0^{z_1-1}\hat{w}0^{z_2}$ by the order that we added the words in this necklace.
+\item [Second Case:] If $w=\sigma u 0^{z(k)}v$ such that $v\sigma u=\hat{w}$ we have that
+\begin{itemize}
+	\item $w$ precedes $v \sigma u 0^{z(k)}$ because the latter is last on its necklace.
+	\item $v \sigma u 0^{z(k)}$ precedes $\sigma u 0^{z(k)+|v|}$ because...
+	\item $\sigma u 0^{z(k)+|v|}$ precedes $0(\sigma+1) u 0^{z(k)+|v|-1}$ because...
+	\item $0(\sigma+1) u 0^{z(k)+|v|-1}$ precedes the word $u_2 (\sigma+1) u_1$ such that $u_1u_2=u0^{z(k)+|v|+1}$ and $last(u_2 (\sigma+1) u_1)$, by the order of the enumeration of the words in this necklace.
+	\item $u_2 (\sigma+1) u_1$ precedes $0(\sigma+1)u_1 0^{|u_2|-1}$ because...
+	\item $0(\sigma+1)u_1 0^{|u_2|-1}$ precedes $0 \tau_2 \dots \tau_l (\sigma+1)u_1$ where $u_2=\tau_1\dots\tau_l \sigma u_1=v\sigma u 0^{z(k)}$ because... 
+	\item $0 \tau_2 \dots \tau_l (\sigma+1)u_1$ precedes $\tau_2 \dots \tau_l (\sigma+1)u_1\tau_1$ because... 
+	\item $\tau_2 \dots \tau_l (\sigma+1)u_1\tau_1$ precedes $(\sigma+1)u_1\tau_1 \tau_2 \dots \tau_l=(\sigma+1) u 0^{z(k)}v$ because... 
+\end{itemize}
+\end{description}
+
+\end{proof}
+
+\section{Forward and backwards transformations}
 
@@
 \end{definition}
-
-\section{Forward and backwards transformations}
 
@@
 \begin{proposition}
-For a word $w=w(i)$ be the $i$th word in the above enumeration.
-Let $l$ be the number of leading zeros in $w$ and let $\hat{w}=\rl{b_1(b^*(w))}{l}$.
-Then, inserting the cycle $\T{\rl{b_1(w)}{s}}_{s=0}^{n-1}$ after the word $\hat{w}_{1..(n-l)}0^l$ in $\T{u(j)}_{j=0}^{i-1}$ yields the sequence $\T{u(j)}_{j=0}^{i}$.
+	Let $w=w(i)$ for some $i$ and let $l$ be the number of leading zeros in $w$.
+	Then, inserting the cycle $\T{R^{-l-n-1}(w),\dots,R^{-l}(w)}$ to $\T{u(j)}_{j=0}^{i-1}$
+	after the word obtained from $R^{-l}(w)$ by decreasing its first letter by one
+	yields the sequence $\T{u(j)}_{j=0}^{i}$.
 \end{proposition}
@@
 
-We look now at ù rotation of $w$, $w'=(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+2})$. Since $w\in L_n$, $w$ is lexicographically larger than $w'$ and in particular,
+We look now at a rotation of $w$, $w'=(z_2(z_1z_2)^{t+1})\dots(z_2(z_1z_2)^{t+2})$. Since $w\in L_n$, $w$ is lexicographically larger than $w'$ and in particular,
 $(z_1z_2z_2(z_1z_2)^{t+1})\geq_{lex}(z_2(z_1z_2)^{t+2})$ which implies that

### 2016-12-22 infdebruijn.tex
With Gal's section

@@
 \end{proposition}
-\begin{proof}
-Let $k$ be a key word  of the form $0^z(k)\hat{w}$. We will prove the proposition for every rotation of $k$:
-
-\begin{description} 
-\item [First Case:] If $w=0^{z_1}\hat{w}0^{z_2}$ such that $z_1+z_2=z(k)$ and $z_1 \neq 0$ then we have that $w$ precedes  $w_1=0^{z_1-1}\hat{w}0^{z_2}1$ by the definition of $nxt$ and that $w_1$ precedes $1 0^{z_1-1}\hat{w}0^{z_2}$ by the order that we added the words in this necklace.
-\item [Second Case:] If $w=\sigma u 0^{z(k)}v$ such that $v\sigma u=\hat{w}$ we have that
-\begin{itemize}
-	\item $w$ precedes $v \sigma u 0^{z(k)}$ because the latter is last on its necklace.
-	\item $v \sigma u 0^{z(k)}$ precedes $\sigma u 0^{z(k)+|v|}$ because...
-	\item $\sigma u 0^{z(k)+|v|}$ precedes $0(\sigma+1) u 0^{z(k)+|v|-1}$ because...
-	\item $0(\sigma+1) u 0^{z(k)+|v|-1}$ precedes the word $u_2 (\sigma+1) u_1$ such that $u_1u_2=u0^{z(k)+|v|+1}$ and $last(u_2 (\sigma+1) u_1)$, by the order of the enumeration of the words in this necklace.
-	\item $u_2 (\sigma+1) u_1$ precedes $0(\sigma+1)u_1 0^{|u_2|-1}$ because...
-	\item $0(\sigma+1)u_1 0^{|u_2|-1}$ precedes $0 \tau_2 \dots \tau_l (\sigma+1)u_1$ where $u_2=\tau_1\dots\tau_l \sigma u_1=v\sigma u 0^{z(k)}$ because... 
-	\item $0 \tau_2 \dots \tau_l (\sigma+1)u_1$ precedes $\tau_2 \dots \tau_l (\sigma+1)u_1\tau_1$ because... 
-	\item $\tau_2 \dots \tau_l (\sigma+1)u_1\tau_1$ precedes $(\sigma+1)u_1\tau_1 \tau_2 \dots \tau_l=(\sigma+1) u 0^{z(k)}v$ because... 
-\end{itemize}
-\end{description}
-
-\end{proof}
 
@@
 \begin{theorem}
-$w^\infty$ is an infinite De-Bruijn sequence.
+	$w^\infty$ is an infinite de Bruijn sequence.
 \end{theorem}
@@
 
+\section{Constructing an Infinite de Bruijn Cycle}
+
+A key word is a word of length $n$ that is maximal in right-to-left (Arabic) lexicographic order among its cyclic rotations.
+Let $kw_0,kw_1,kw_2,\dots$ be an enumeration of all key-words, ordered in right-to-left (Arabic) lexicographic order.
+Let $C_m=\{R^i(kw_m): i=1,\dots,n\}$ be the cycle of $kw_m$.
+We order the elements of $C_m$ as follows:  if $kw_m=0^l(\sigma+1)w$, then $w0^l(\sigma+1)$ is the first word in $C_m$, and each word $w'$ is followed by $R(w')$.
+The last word in $C_m$ is $(\sigma+1)w0^l$.\\
+
+For each $m<n$ we define a de Bruijn sequence $D_m$, over the words $\bigcup_{i=0}^m C_i$ as follows: 
+\begin{itemize}
+	\item $D_0=0^n$.
+	\item If $kw_{m+1}=0^l(\sigma+1)w$, then $D_{m+1}$ is obtained by inserting the sequence $C_{m+1}$ after the word $\sigma w 0^l\in C_m$.
+\end{itemize}
+
+%\begin{lemma}
+%Every $D_m$ is a de Bruijn sequence over $\bigcup_{i=0}^m C_i$, and   $\forall m$ $\exists k$ so that if $k\leq r$, then $D_m$ is a prefix of $D_r$. 
+%\end{lemma}
+
+\begin{definition}
+	For $w,w\in \N^n$ and $m\in \N$, write $w<_m w'$ if $w$ appears before $w'$ in $D_m$. Write $<=\bigcup_{i=0}^\infty$.
+\end{definition}
+
+For a word $w$, $max(w)$ is the maximal number in $w$.
+
+\begin{lemma}
+	If $w<w'$, then $max(w)\leq max(w')$.
+\end{lemma}
+
+\begin{corrolary}
+	$<$ defines an infinite de Bruijn sequence.
+\end{corrolary}
+
+\begin{proof}
+	By the previous Lemma, each word is preceded by finitely many words thus $<$ defines an infinite sequence.
+Since each $D_m$ is a de Bruijn sequence and since $<_m\subseteq<_{m+1}$, the sequence defined by $<$ is a de Bruijn sequence.
+\end{proof}
+
+Let $D$ be the infinite de Bruijn sequence defined by $<$.
+
+\begin{theorem}
+	For a  word $\sigma w$ in $D$, let $nxt(\sigma w)$ be the successor of $\sigma w$ in $D$. Then,
+	$$nxt(\sigma w)=\left\{ \begin{array}{lr}
+	w(\sigma+1), & last((\sigma+1)w)\\
+	w0, & last(\sigma w)\\
+	w\sigma, & otherwise
+	\end{array}\right.$$
+\end{theorem}
+
+\begin{definition}
+	If $kw_m=0^l(\sigma+1)w$, we write $first(w0^l(\sigma+1))$, $key(0^l(\sigma+1)w)$ and $last((\sigma+1)w0^l)$.
+In addition, for a cycle $C_m$, $first(C_m)=w\in C_m$ so that $first(w)$,  $key(C_m)=kw_m$ and $last(C_m)=w\in C_m$ so that $last(w)$.
+\end{definition}
+
+\begin{lemma}
+	For any $w'\in C_m$, $first(C_m)\leq w'\leq last(C_m)$.
+\end{lemma}
+\begin{proof}
+	This the way we ordered the cycles.
+\end{proof}
+
+\begin{definition}
+	We say that $C_{i_0}C_{i_1}\dots C_{i_k}$ is a sequence of cycles, if for every $j<k$, $nxt(last(C_{i_j}))=first(C_{i_{j+1}})$.
+\end{definition}
+
+\begin{lemma}
+	\label{sequence}
+	Let $C_{i_0}C_{i_1}\dots C_{i_k}$ be a sequence of cycles. Write, $key(C_{i_0})=0^l(\sigma)w$ where $\sigma\neq 0$. Then, for every $j\leq k$, $key(C_{i_j})=0^l(\sigma+j)w$.
+\end{lemma}
+
+\begin{proof}
+	Assume by induction that $key(C_{i_j})=0^l(\sigma+j)w$ for $j<k$.
+Hence, $last(C_{i_j})=(\sigma+j)w0^l$.
+Thus, $nxt((\sigma+j)w0^l)=w0^l(\sigma+j+1)$ or $nxt((\sigma+j)w0^l)=w0^{l+1}$.
+Since $\neg(first(w0^{l+1}))$, we have
+	$$nxt((\sigma+j)w0^l)=w0^l(\sigma+j+1)=first(C_{i_{j+1}}).$$
+	We conclude that $key(C_{i_{j+1}})=0^l(\sigma+j+1)w$.
+\end{proof}
+
+\begin{lemma}[The parentheses property]
+	\label{parenthesis}
+	For any two cycles $C_k$ and $C_m$, one of the following occur
+	\begin{itemize}
+		\item $last(C_k)<first(C_m)$ or $last(C_m)<first(C_k)$.
+
+		\item $first(C_k)<first(C_m)\leq last(C_m)<last(C_k)$ or \\
+		$first(C_m)<first(C_k)\leq last(C_k)<last(C_m)$.
+	\end{itemize}
+\end{lemma}
+\begin{proof}
+	This concluded by the way $D_{m+1}$ is obtained from $D_m$.
+\end{proof}
+
+\begin{definition}
+	We say that $C_m$ is embedded in $C_k$ if $first(C_k)<first(C_m)\leq last(C_m)<last(C_k)$.\\ 
+	In addition, $C_m$ is said to be immediately embedded in $C_k$ if there is no $C_l$ such that $C_m$ is embedded in $C_l$ and $C_l$ is embedded in $C_k$.\\ 
+	We define by inductively the statement: ``$C_m$ is $r$-embedded in $C_k$":
+	\begin{itemize}
+		\item $C_m$ is $1$-embedded in $C_k$ if it is immediately embedded in $C_k$.
+		\item $C_m$ is $r$-embedded in $C_k$ if there is a cycle $C_l$ such that $C_m$ is $r-1$-embedded in $C_l$ and $C_l$ is immediately embedded in $C_k$. 
+	\end{itemize} 
+\end{definition}
+
+\begin{lemma}
+	\label{embedding-properties}
+	Assume that $C_m$ is immediately embedded $C_k$. Write $key(C_m)=0^i(\sigma+1)0^jw$ where $w$ does not starts with $0$. Then,
+	\begin{itemize}
+		\item $key(C_k) =0^{i+1+j}w$.
+		\item If $u\in C_k$ and $last(C_m)<u$, then $u=0^{j_2}w0^{i+1+j_1}$ where $j_1+j_2=j$. 
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+	To prove the first item, note that since $0^i(\sigma+1)0^jw$ is maximal among its rotations, the same holds for $0^{i+1+j}w$. Thus, we need to show that $0^{i+1+j}w\in C_k$.
+
+	Take a maximal sequence of cycles that begins in $C_m$ and let $C_{m+r}$ be the last cycle in this sequence.
+By lemma \ref{sequence}, $key(C_{m+r})=0^i(\sigma+1+r)0^jw$.
+By the parentheses property, $C_{m+r}$ is immediately embedded in $C_k$.
+And finally, by the maximality of the sequence of cycles, $nxt(last(C_{m+r}))\in C_k$.
+
+	As a result, we have:
+	$$nxt(last(C_{m+r}))=nxt((\sigma+1+r)0^jw0^i)\in\{\ 0^jw0^i0, 0^jw0^i(\sigma+2+r)\}.$$ If $nxt((\sigma+1+r)0^jw0^i)= 0^jw0^i(\sigma+2+r)$, then $last((\sigma+2+r)0^jw0^i)$ which implies $first(0^jw0^i(\sigma+2+r))$.
+But $first(last(C_{m+r}))$ contradicts the maximality of our sequence of cycles.
+Hence, $nxt((\sigma+1+r)0^jw0^i)= 0^jw0^i0\in C_k$.
+Now, $0^{i+1+j}w$ is a rotation of $0^jw0^i0$ thus $0^{i+1+j}w\in C_k$ as required.
+
+	For proving the second item, we note that $last(C_k)=w0^{i+1+j}$.
+As we have seen, the first element in $C_k$ that follows $C_m$ (and follows $C_{m+r}$) is $nxt(last(C_{m+r}))= 0^jw0^i0$.
+As a result, if $u\in C_k$ and $last(C_m)<u$, then
+	$$0^jw0^i0\leq u \leq w0^{i+1+j}$$
+	which implies that $u=0^{j_2}w0^{i+1+j_1}$
+\end{proof}
+
+\begin{corrolary}
+	\label{embedding-deletes-zeroes}
+	Assume that $C_m$ is $r$-embedded in $C_k$. Write $key(C_m)=uv$ where $u$ is the minimal prefix of $key(C_m)$ that includes $r$ non-zero numbers. Then, $key(C_k)=0^{|u|}v$.
+\end{corrolary}
+
+\begin{proof}
+	By $r$ invocations of the first item of the previous lemma.
+\end{proof}
+
+\begin{lemma}
+	\label{first-ordering}
+	For every $m\in\N$, $first(C_m)<first (C_{m+1})$.
+\end{lemma}
+
+\begin{proof}
+	TBD
+\end{proof}
+
+\begin{theorem}
+	For any word $\tau w$, $\tau w<(\tau+1)w$.
+\end{theorem}
+
+\begin{proof}
+	Fix an arbitrary cycle $C_m$.
+We show that if $(\tau+1)w\in C_m$.
+Then, $\tau w<(\tau+1)w$.
+We start by showing this fact for $last(C_m)$.
+Write $key(C_m)=0^l(\sigma+1)w'$ and hence, $last(C_m)=(\sigma+1)w'0^l$ and $first(C_m)=w'0^l(\sigma+1)$.
+Write $pre=nxt^{-1}$ and note that $pre(w'0^l(\sigma+1))=\sigma w'0^l$.
+Hence, we get that
+	$$\sigma w' 0^l<(\sigma+1)w'0^l.$$
+
+	Now we deal with the general case in which $(\tau+1)w\neq last(C_m)$. We write 
+	$key(C_m)=0^l(\sigma+1)w_1(\tau+1)w_2$, where $$(\tau+1)w=(\tau+1)w_20^l(\sigma+1)w_1.$$ Let $C_k$ be the cycle of $\tau w$.
+Since every rotation of $\tau w$ is lexicographically smaller than some rotation of $(\tau+1)w$, we have $key(C_k)<_{lex}key(C_m)$.
+Hence, $k<m$ and by Lemma \ref{first-ordering}, we get
+	$$first(C_k)<first(C_m).$$
+
+	Now, if $last(C_k)<first(C_m)$ then every element of $C_k$ precedes every element of $C_m$ and we are done.
+Otherwise, by the parentheses property, $C_m$ is embedded in $C_k$.
+Note that $|(\tau+1)w|_0-|\tau w|_0\in\{0,1\}$.
+Use corollary \ref{embedding-deletes-zeroes} to conclude that $|(\tau+1)w|_0-|\tau w|_0=1$ and that $C_m$ is immediately embedded in $C_k$.
+Moreover, note that as $|(\tau+1)w|_0-|\tau w|_0=1$, we have $\tau=0$.
+
+	According to our conclusions, we can write: $key(C_m)=0^l(\sigma+1)w_11w_2$. We write $w_1=0^jw_1'0^i$ and $w_2=0^rw_2'$ where $w_1'$ and $w_2'$ do not start or end with zero. We have,
+	$$key(C_m)=0^l(\sigma+1)0^jw_1'0^i10^rw_2'.$$
+	Assume for a contradiction that $(\tau+1)w<\tau w$.
+Recall that $\tau w\in C_k$ and that $C_m$ is immediately embedded in $C_k$, and conclude that $last(C_m)<\tau w\leq last(C_k)$.
+Therefore, by Lemma \ref{embedding-properties}, $\tau w=0^{j_2}w_1'0^i10^rw_2'0^{l+1+j_1}.$ Thus, we have:
+	\begin{equation}
+	\label{1}
+	0^{j_2}w_1'0^i10^rw_2'0^{l+1+j_1}=0^{r+1}w_2'0^l(\sigma+1)0^jw_1'0^i.
+	\end{equation}
+	Since also $|0^{j_2}w_1'0^i10^rw_2'0^{l+1+j_1+1}|_1 = |0^{r+1}w_2'0^l(\sigma+1)0^jw_1'0^i|_1$ we get $\sigma+1=1$. Hence,
+
+	\begin{equation}
+	\label{2}
+	key(C_m)=0^l10^jw_1'0^i10^rw_2'
+	\end{equation}
+
+	and Equation \ref{1} can be rewritten as follows:
+
+	\begin{equation}
+	\label{3}
+	0^{j_2}w_1'0^i10^rw_2'0^{l+1+j_1}=0^{r+1}w_2'0^l10^jw_1'0^i.
+	\end{equation}
+
+	For the rest of the proof we assume that $w_1'\neq\varepsilon$ and $w_2'\neq \varepsilon$. The other cases are dealt similarly\footnote{really! I checked !}.
+	By deleting the initial and final segments of zeroes, we get from Equation \ref{3},
+	\begin{equation}
+	\label{4}
+	j_2=r+1, \ \ w_1'0^i10^rw_2'=w_2'0^l10^jw_1'.
+	\end{equation}
+	Now, by Equation \ref{2}, 
+	\begin{equation}
+	\label{5}
+	0^l10^jw_1'0^i10^rw_2'\geq_{lex} 0^i10^rw_2'0^l10^{j}w_1'.
+	\end{equation}
+	By combining equations \ref{4} and \ref{5}, we get 
+	\begin{equation}
+	0^l10^j\geq_{lex}0^i10^r.
+	\end{equation}
+	Hence, $j\leq r$ and in particular, $j_2\leq r$ in contradiction to Equation \ref{4}.
+\end{proof}
+
 \end{document}

### 2016-12-22 infdebruijn.tex
...

@@
 Let $kw_0,kw_1,kw_2,\dots$ be an enumeration of all key-words, ordered in right-to-left (Arabic) lexicographic order.
-Let $C_m=\{R^i(kw_m): i=1,\dots,n\}$ be the cycle of $kw_m$.
+Let $C_m=\{R^i(kw_m): i=1,\dots,n\}$ be the necklace of $kw_m$.
 We order the elements of $C_m$ as follows:  if $kw_m=0^l(\sigma+1)w$, then $w0^l(\sigma+1)$ is the first word in $C_m$, and each word $w'$ is followed by $R(w')$.
@@
 
-For each $m<n$ we define a de Bruijn sequence $D_m$, over the words $\bigcup_{i=0}^m C_i$ as follows: 
+For each $m \in \N$ we define a de Bruijn sequence $D_m$, over the words $\bigcup_{i=0}^m C_i$ recursively by:
 \begin{itemize}
 	\item $D_0=0^n$.
-	\item If $kw_{m+1}=0^l(\sigma+1)w$, then $D_{m+1}$ is obtained by inserting the sequence $C_{m+1}$ after the word $\sigma w 0^l\in C_m$.
+	\item If $kw_{m+1}=0^l(\sigma+1)w$, then $D_{m+1}$ is obtained by injecting the sequence $C_{m+1}$ between the word $\sigma w 0^l$ and its follower in $C_m$.
 \end{itemize}
@@
 \begin{definition}
-	For $w,w\in \N^n$ and $m\in \N$, write $w<_m w'$ if $w$ appears before $w'$ in $D_m$. Write $<=\bigcup_{i=0}^\infty$.
+	For $w,w\in \N^n$ and $m\in \N$, write $w<_m w'$ if $w$ appears before $w'$ in $D_m$. Let $<$ be the union $\bigcup_{i=0}^\infty <_i$.
 \end{definition}

### 2016-12-25 infdebruijn.tex
With a proof that the firsts are ordered lexicographically

--- 2016-12-22 infdebruijn.tex
@@
 
-A key word is a word of length $n$ that is maximal in right-to-left (Arabic) lexicographic order among its cyclic rotations.
-Let $kw_0,kw_1,kw_2,\dots$ be an enumeration of all key-words, ordered in right-to-left (Arabic) lexicographic order.
-Let $C_m=\{R^i(kw_m): i=1,\dots,n\}$ be the cycle of $kw_m$.
-We order the elements of $C_m$ as follows:  if $kw_m=0^l(\sigma+1)w$, then $w0^l(\sigma+1)$ is the first word in $C_m$, and each word $w'$ is followed by $R(w')$.
+A key word is an $n$-length word that is (arabic) maximal among its rotations.
+Let $kw_0,kw_1,kw_2,\dots$ be an enumeration of all key-words, ordered lexicographically.
+Let $C_m$ be the cycle of $kw_m$.
+We order the elements of $C_m$ as follows:  if $kw_m=0^l(\sigma+1)w$, then $w0^l(\sigma+1)$ is the first sequence in $C_m$, and each word $w'$ is followed by $R(w')$.
 The last word in $C_m$ is $(\sigma+1)w0^l$.\\
@@
 	For a  word $\sigma w$ in $D$, let $nxt(\sigma w)$ be the successor of $\sigma w$ in $D$. Then,
-	$$nxt(\sigma w)=\left\{ \begin{array}{lr}
-	w(\sigma+1), & last((\sigma+1)w)\\
-	w0, & last(\sigma w)\\
-	w\sigma, & otherwise
+	$$nxt(\sigma w)=\left\{ \begin{array}{ll}
+	w(\sigma+1) & \text{if }last((\sigma+1)w);\\
+	w0          & \text{if } last(\sigma w);\\
+	w\sigma     & \text{otherwise}
 	\end{array}\right.$$
@@
 \begin{definition}
-	We say that $C_m$ is embedded in $C_k$ if $first(C_k)<first(C_m)\leq last(C_m)<last(C_k)$.\\ 
+	We say that $C_m$ is embedded in $C_k$, if $C_m=C_k$ or $first(C_k)<first(C_m)\leq last(C_m)<last(C_k)$.\\ 
 	In addition, $C_m$ is said to be immediately embedded in $C_k$ if there is no $C_l$ such that $C_m$ is embedded in $C_l$ and $C_l$ is embedded in $C_k$.\\ 
@@
 	\begin{itemize}
-		\item $C_m$ is $1$-embedded in $C_k$ if it is immediately embedded in $C_k$.
+		\item $C_m$ is $0$-embedded in $C_k$ if $C_m=C_k$.
 		\item $C_m$ is $r$-embedded in $C_k$ if there is a cycle $C_l$ such that $C_m$ is $r-1$-embedded in $C_l$ and $C_l$ is immediately embedded in $C_k$. 
@@
 	$$nxt(last(C_{m+r}))=nxt((\sigma+1+r)0^jw0^i)\in\{\ 0^jw0^i0, 0^jw0^i(\sigma+2+r)\}.$$ If $nxt((\sigma+1+r)0^jw0^i)= 0^jw0^i(\sigma+2+r)$, then $last((\sigma+2+r)0^jw0^i)$ which implies $first(0^jw0^i(\sigma+2+r))$.
-But $first(last(C_{m+r}))$ contradicts the maximality of our sequence of cycles.
+But $first(nxt(last(C_{m+r})))$ contradicts the maximality of our sequence of cycles.
 Hence, $nxt((\sigma+1+r)0^jw0^i)= 0^jw0^i0\in C_k$.
@@
 \begin{lemma}
+	\label{both-embedded}
+	Assume that $last(C_k)<first(C_m)$ and $C_k,C_m$ are both immediately embedded in a cycle $C$.
+Write $key(C_k)=0^lw$ where $w$ starts with a non-zero letter.
+Then, $key(C_m)=0^lw'$ where $w<_{lex}w'$.
+\end{lemma}
+\begin{proof}
+	First, if there is a sequence of cycles from $C_k$ and $C_m$, the claim follows from Lemma \ref{sequence}. Otherwise, there is some $u\in C$ such that
+	$$last(C_k)<u<first(C_m).$$
+	Consider a  maximal sequence of cycles that starts with $C_k$.
+This sequence ends in some cycle $C_{k'}$.
+Similarly, consider a maximal sequence of cycles that ends in $C_m$ and let $C_{m'}$ be the first element in this sequence.
+Therefore,
+	$$last(C_{k'}) <v<first(C_{m'})\Longrightarrow v\in C.$$
+
+	Write $key(C_k)=0^l(\sigma+1)w_1$ (namely, $w=(\sigma+1)w_1$) and write  $w_1=0^jw_2$ where $w_2$ starts with non-zero letter. Hence, 
+	\begin{equation}
+	\label{ck}
+	key(C_k)=0^l(\sigma+1)0^jw_2.
+	\end{equation}
+	By Lemma \ref{sequence}, $key(C_{k'})=0^l(\sigma+1+r)0^jw_2$, and hence $last(C_{k'})=(\sigma+1+r)0^jw_20^l$. Let $u_1$ be the successor of $last(C_{k'})$. Thus,
+	$$u_1=0^jw_20^{l+1}.$$
+	Now, let $u_2$ be the predecessor of $first(C_{m'})$. Thus,
+	$$u_2=0^{j_2}w_20^{l+1+j_1}, \text{ where } j_1+j_2=j.$$
+	In addition, since $C_{m'}$ is embedded in $C$, $u_2\neq last(C)$ thus $j_2>0$. As a result, $$first(C_{m'})=0^{j_2-1}w_20^{l+1+j_1}1.$$
+	We get that $key(C_{m'})=0^{l+1+j_1}10^{j_2-1}w_2$. Hence, by Lemma \ref{sequence}, 
+	\begin{equation}
+	\label{cm}
+	key(C_m)=0^{l+1+j_1}(1+t)0^{j_2-1}w_2.
+	\end{equation}
+	By Equation \ref{ck}, $w=(\sigma+1)0^{j}w_2$. By Equation \ref{cm}, $w'=0^{1+j_1}(1+t)0^{j_2-1}w_2$. We see that indeed $w<_{lex}w'$.
+\end{proof}
+
+\begin{lemma}
 	\label{first-ordering}
-	For every $m\in\N$, $first(C_m)<first (C_{m+1})$.
+	If $k<m$, then $first(C_k)<first (C_m)$.
 \end{lemma}
@@
 \begin{proof}
-	TBD
+	Since $<$ is a linear ordering, we can prove an equivalent statement: $$first(C_k)<first(C_m) \Longrightarrow k<m.$$ We take such cycles $C_k$ and $C_m$.
+By the parentheses property, either $C_m$ is embedded in $C_k$, or $C_m$ is entirely after $C_k$.
+If $C_m$ is embedded in $C_k$, by Corollary \ref{embedding-deletes-zeroes} we get that $k<m$.
+It is left to deal with the case that $last(C_k)<first(C_m)$.
+We consider two cases.
+	\begin{description}
+		\item[Case 1.] $C_k$ and $C_m$ are both embedded in some cycle $C$.
+
+		In this case, we can find cycles $C_{k'}$ and $C_{m'}$ such that
+		\begin{enumerate}
+			\item $C_k$ is embedded in $C_{k'}$ and $C_{m}$ is embedded in $C_{m'}$
+
+			\item $C_{k'}$ and $C_{m'}$ are immediately embedded in $C$.
+
+		\end{enumerate}
+
+		By item 1 and Lemma~\ref{embedding-deletes-zeroes}, we can write $key(C_k)=uv$ and $key(C_{k'})=0^{|u|}v$. Write 
+		$$v=0^lv_1$$ 
+		where $v_1$ starts with a non-zero letter thus $key(C_{k'})=0^{|u|+l}v_1$. By item~2 and Lemma~\ref{both-embedded}, $key(C_{m'})=0^{|u|+l}v_2$ where 
+		$$v_1<_{lex}v_2.$$
+
+		Write $v_2=0^r v_2'$ where $v_2'$ starts with a non zero letter. Hence, $$v_1=xv_1'$$ 
+		where $|x|=r$, $|v_1'|=|v_2'|$, and 
+		$$v_1'<_{lex} v_2'.$$
+		Since $key(C_{m'})=0^{|u|+l}v_2 =0^{|u|+l+r}v_2'$, by item~2 and Lemma \ref{embedding-deletes-zeroes}, $key(C_m)=u'v_2'$.
+Recall that $key(C_k)=uv=u0^lv_1=u0^lxv_1'$.
+Since $v_1'<_{lex}v_2'$, $key(C_k)<_{lex}key(C_m)$ thus $k<m$ as required.
+
+		\item[case 2.] There is no cycle $C$ such that $C_k$ and $C_m$ are embedded in $C$.
+
+		Take a cycle $C_{k'}$ such that $C_k$ is $r_1$-embedded in $C_{k'}$ and $r_1$ is maximal with respect to this property.
+Similarly, take a cycle $C_{m'}$ such that $C_{m}$ is $r_2$-embedded in $C_{m'}$ and $r_2$ is maximal as possible.
+By the parentheses property, $C_{k'}$ is entirely before $C_{m'}$.
+$C_{k'}$ and $C_{m'}$ are not embedded in any cycle so there is a sequence of cycles from $C_{k'}$ to $C_{m'}$.
+Write $key(C_k)=u(\sigma+1)v$ such that $key(C_{k'})=0^{|u|}(\sigma+1)v$ (by Lemma \ref{embedding-deletes-zeroes}).
+Hence, $key(C_{m'})=0^{|u|}(\sigma+1+r)v$ where $r>1$ (by Lemma \ref{sequence}).
+Finally, by Lemma \ref{embedding-deletes-zeroes} we get $key(C_m)=u'(\sigma+1+r)v$.
+We see that $key(C_k)=u(\sigma+1)v<_{lex}u'(\sigma+1+r)v=key(C_m)$.
+Therefore, $k<m$.
+
+	\end{description}
 \end{proof}

### 2016-12-25 paper.tex
With a proof that the firsts are ordered lexicographically

\documentclass{article}
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}

%\IEEEoverridecommandlockouts        % This command is only needed if you want to use the \thanks command
%\overrideIEEEmargins                        % See the \addtolength command later in the file to balance the column lengths

% Name clashes workaround
%\makeatletter
%\let\IEEEproof\proof
%\let\IEEEendproof\endproo f
%\let\proof\@undefined
%\let\endproof\@undefined
%\makeatother

\usepackage{epsfig} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}  
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{automata,arrows,decorations.pathmorphing,decorations.markings,positioning}
\usetikzlibrary{shapes}
%\usepackage{balance}
\usepackage{scrextend}
\addtokomafont{labelinglabel}{\sffamily}

% Theorem like env.
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}     
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{corrolary}[theorem]{Corrolary}

%\newcommand{\RotateLeft}{rlft}
\DeclareMathOperator{\RotateLeft}{RotLft}

%------------------------------------------- preamble ---------------------------

\newcommand{\R}{{\mathbb{R}}}
\newcommand{\N}{{\mathbb{N}}}
\newcommand{\Z}{{\mathbb{Z}}}

\newcommand{\REF}[2]{#1~\ref{#2}}

\newcommand{\T}[1]{\langle{#1}\rangle}
\newcommand{\rr}[2]{R^{#2}({#1})}
\newcommand{\rl}[2]{R^{-{#2}}({#1})}

\newcommand{\AorB}[2]{\bigl(#2\text{?}A(#1)\text{:}B(#1)\bigr)}

\usepackage{amssymb} 
\usepackage{algpseudocode,algorithm}
\usepackage{subfigure}

%\pagestyle{plain}

\title{An Infinite de Bruijn Sequence}

\author{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\section{Introduction}

A $k$-ary de Bruijn sequence of span $n$ is a cyclic sequence of length $k^n$ in which each $k$-ary string of length $n$ appears exactly once as
a substring. A well known construction of such a sequence was proposed by Ford ~\cite{Ford57} as follows:

\begin{algorithm}
Repeatedly append the symbol $k-1$ if the word formed by the $n$ most recent symbols (padded with zeros on the left, if not enough symbols exist) is new, otherwise append $k-2$, otherwise $k-3$, etc. Stop after appending $n$ consecutive zeros. 
\caption{The prefer-max construction.}
\end{algorithm}

For example, if we choose $k=3$ and $n=3$ we get the sequence:
$$\langle2,2,2,1,2,2,0,2,1,1,2,1,0,2,0,1,2,0,0,1,1,1,0,1,0,0,0\rangle.$$
Note that this sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$ as substrings. Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).

The first result of this paper, that we call the Onion lemma, is that this is not a coincidence:

\begin{theorem}[Onion]
	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$. Furthermore, the suffix that begins with the 
	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
\end{theorem}

This observation lead us to look at the reverse of the prefer-max sequence. The structure that we have identified means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then $\{0,1,2\}^n$, and so on.

The second contribution of this work is then an efficient construction of this reversed sequence, as formulated in Algorithm~\ref{inf-construction}. Note that each step of this construction can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).

\begin{algorithm}[!h]
	Append $n$ zeros. Then, repeatedly, let $\sigma w$ be the word formed by the $n$ most recent symbols. Append $\sigma+1$ if $(\sigma+1)w$ is of the form $u0^l$ where $0^lu$ is maximal in right-to-left lexicographic order among all of its rotations. If $(\sigma+1)w$ is not of that form and $\sigma w$ is, append the symbol $0$. Otherwise, if neither $(\sigma+1)w$ nor $(\sigma)w$ are of that form, append $\sigma$.
	\caption{An infinite de Bruijn sequence.}
	\label{inf-construction}
\end{algorithm}

The fact that this generates the reverse of the prefer-max sequence is the next contribution of this paper:

\begin{theorem} 
The first $k^n$ symbols generated by Algorithm~\ref{inf-construction} form the reverse of the word generated by the prefer-max construction with the parameters $k$ and $n$.	
\end{theorem}

While our main focus is on analyzing the reversed word, we also have a result about the prefer-max sequence itself. Our result gives the first (to our knowledge) efficient construction for that sequence:

\begin{algorithm}[!h]
	Append $n-1$ zeros and then the symbol $k$. Then, repeatedly, let $\sigma w$ be the word formed by the $n$ most recent symbols. Append the symbol $\sigma-1$  if $\sigma w$  is of the form specified in Algorithm~\ref{inf-construction}. Otherwise, if there is a maximal $\sigma'$ such that $\sigma'w$ is of that form, append the symbol $\sigma'$. Otherwise, if there is no such $\sigma'$, append the symbol $\sigma$.

	\caption{An efficient construction of the prefer-max sequence.}
	\label{efficient-pref-max}
\end{algorithm}

Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.

\end{document}

### 2016-12-25 paper.tex
...

@@
 
-While our main focus is on analyzing the reversed word, we also have a result about the prefer-max sequence itself.
+In particular, the above theorem says that the sequence generated by Algorithm~\ref{inf-construction} is a de Bruijn sequence, i.e., that each word in $\N^n$ appears exactly once as a substring.
+
+While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself.
 Our result gives the first (to our knowledge) efficient construction for that sequence:
@@
 
-Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.
+Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.
+
+\begin{theorem}
+	The sequence generated by Algorithm~\ref{efficient-pref-max} is the prefer-max sequence with parameters $k$ and $n$.
+\end{theorem}
+
+The main tool that brought us to the above results is a formulation of an alternative description of the infinite sequence. For this, we need to introduce some language.
+
+The de Bruijn graph
 

### 2016-12-26 paper.tex
...

@@
 Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
-
 The first result of this paper, that we call the Onion lemma, is that this is not a coincidence:
@@
 This observation lead us to look at the reverse of the prefer-max sequence.
-The structure that we have identified means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then $\{0,1,2\}^n$, and so on.
+The structure that we have identified means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
 
@@
 
-The fact that this generates the reverse of the prefer-max sequence is the next contribution of this paper:
+The fact that this generates the reverse of the prefer-max sequence is formulated in the following theorem:
 
 \begin{theorem} 
-The first $k^n$ symbols generated by Algorithm~\ref{inf-construction} form the reverse of the word generated by the prefer-max construction with the parameters $k$ and $n$.	
+The first $k^n$ symbols generated by Algorithm~\ref{inf-construction} form the reverse of the sequence generated by the prefer-max construction with the parameters $k$ and $n$.	
 \end{theorem}
@@
 
-Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.
+Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word (see Proposition~\ref{efficiency-of-pref-max} below).
+The fact that this is indeed the prefer-max sequence is stated in the following theorem:
 
@@
 
-The de Bruijn graph
-
 \end{document}

### 2016-12-26 paper.tex
...

@@
 	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
+	\label{thm:onion}
 \end{theorem}
@@
 This observation lead us to look at the reverse of the prefer-max sequence.
-The structure that we have identified means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
+The structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
 
-The second contribution of this work is then an efficient construction of this reversed sequence, as formulated in Algorithm~\ref{inf-construction}.
+The second contribution of this work is then an efficient construction of this reversed sequence.
+This is formulated in Algorithm~\ref{inf-construction}.
 Note that each step of this construction can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).
@@
 
-Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word (see Proposition~\ref{efficiency-of-pref-max} below).
+Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$s which are symbols in $\sigma w$ or are a symbol that smaller by one than a symbol in $\sigma w$ (see Proposition~\ref{efficiency-of-pref-max} below).
 The fact that this is indeed the prefer-max sequence is stated in the following theorem:

### 2016-12-26 paper.tex
added specifically

@@
 This observation lead us to look at the reverse of the prefer-max sequence.
-The structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
+Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
 

### 2016-12-26 paper.tex
...

@@
 This is formulated in Algorithm~\ref{inf-construction}.
-Note that each step of this construction can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).
+We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).
 

### 2016-12-27 paper.tex
...

@@
 \usepackage{subfigure}
+
+\newcommand{\nega}   [1]{\overline{#1}}
+\newcommand{\companion}{comp}
+\newcommand{\shlsame}[1]{shl\text{-}same(#1)}
+\newcommand{\shlopp} [1]{shl\text{-}opp(#1)}
+\newcommand{\shlone} [1]{shl\text{-}one(#1)}
+\newcommand{\shlzero}[1]{shl\text{-}zero(#1)}
+\newcommand{\idx}    [1]{idx(#1)}
 
@@
 While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself.
-Our result gives the first (to our knowledge) efficient construction for that sequence:
+Our result gives the first (to the best of our knowledge) efficient construction for that sequence:
 
@@
 
-The main tool that brought us to the above results is a formulation of an alternative description of the infinite sequence. For this, we need to introduce some language.
+The main tool that brought us to the above results is a formulation of an alternative description of the infinite sequence. For this, we need to introduce some language, as follows.
+
+The $n$ dimensional infinite de Bruijn graph is the graph $G_{n}=\T{V,E}$ where $V=\N^n$ and $E=\{ \T{\sigma_1 w, w \sigma_2} \colon \sigma_1,\sigma_2\in\N, w \in \N^{n-1}\}$.
+The de Bruijn sequences we discussed before are in one-to-one correspondence with the Hamiltonian cycles in the de Bruijn graph, as follows: (1) Concatenating the leftmost bit of the vertices in a cycle produces a de Bruijn sequence of order $n$; and (2) A cycle can be constructed from a de Bruijn sequence $\T{\sigma_1,\dots,\sigma_{2^n}}$ of order $n$ by visiting the vertex $\sigma_1\cdots\sigma_n$, then $\sigma_2\cdots\sigma_{n+1}$ and so on.
+
+A Necklace in the de Bruijn graph $G_n$ is the cycle:
+
+\begin{algorithm}[!h]
+	Start with the cycle $\T{0^n}$.
+The $i$th cycle is constructed by extending the $(i-1)$th cycle as follows: Let $w_i$ be the $i$th smallest key word in right-to-left lexicographic order.
+Let $l$ be the number of leading zeros in $w_i$, i.e., assume that $w_i=0^l\sigma_1 \cdots\sigma_{n-l}$ where $\sigma_1$ is not zero.
+Add the sequence $\sigma_2\cdots\sigma_{l-n}0^l\sigma_1, \sigma_3\cdots\sigma_{l-n}0^l\sigma_1\sigma_2,\dots, \sigma_1\cdots\sigma_{l-n}0^l$ between the word $(\sigma_1-1)\cdots\sigma_{l-n}0^l$ and its follower in the $(i-1)$th cycle.
+
+	\caption{A cycle joining construction.}
+	\label{cycle-joining}
+\end{algorithm}
 

### 2016-12-27 paper.tex
...

--- 2016-12-26 paper.tex
@@
 
+\newcommand{\nega}   [1]{\overline{#1}}
+\newcommand{\companion}{comp}
+\newcommand{\shlsame}[1]{shl\text{-}same(#1)}
+\newcommand{\shlopp} [1]{shl\text{-}opp(#1)}
+\newcommand{\shlone} [1]{shl\text{-}one(#1)}
+\newcommand{\shlzero}[1]{shl\text{-}zero(#1)}
+\newcommand{\idx}    [1]{idx(#1)}
+
 %\pagestyle{plain}
 
-\title{An Infinite de Bruijn Sequence}
+\title{An Efficient Construction of the Prefer-Max Sequence and of an Infinite de Bruijn Sequence}
 
@@
 While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself.
-Our result gives the first (to our knowledge) efficient construction for that sequence:
+Our result gives the first (to the best of our knowledge) efficient construction for that sequence:
 
-\begin{algorithm}[!h]
+\begin{algorithm}
 	Append $n-1$ zeros and then the symbol $k$.
@@
 
-Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$s which are symbols in $\sigma w$ or are a symbol that smaller by one than a symbol in $\sigma w$ (see Proposition~\ref{efficiency-of-pref-max} below).
+Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine for $\sigma'$ only symbols that are $\sigma w$ or are smaller by one than a symbol in $\sigma w$, as we will establish later in the paper.
 The fact that this is indeed the prefer-max sequence is stated in the following theorem:
@@
 
-The main tool that brought us to the above results is a formulation of an alternative description of the infinite sequence. For this, we need to introduce some language.
+A central tool to our analysis of the sequences descibed above is an alternative formulation of the Ford sequence. For this, we need to introduce some language, as follows.
+
+The $n$ dimensional infinite de Bruijn graph is the graph $G_{n}=\T{V,E}$ where $V=\N^n$ and $E=\{ \T{\sigma_1 w, w \sigma_2} \colon \sigma_1,\sigma_2\in\N, w \in \N^{n-1}\}$.
+The de Bruijn sequences, defined in the beginning of this paper, are in one-to-one correspondence with the Hamiltonian cycles in the de Bruijn graph, as follows: (1) Concatenating the first letter of each vertex in a cycle produces a de Bruijn sequence of order $n$; and (2) A cycle can be constructed from a de Bruijn sequence $\T{\sigma_1,\dots,\sigma_{2^n}}$ of order $n$ by visiting the vertex $\sigma_1\cdots\sigma_n$, then $\sigma_2\cdots\sigma_{n+1}$ and so on.
+
+Let $rtl(\sigma_1\sigma_2\dots\sigma_n) = \sigma_2\dots\sigma_n\sigma_1$ denote the rotation of a word to the left and let $rtl^i(w)$ denote a rotation of $i$ letters to the left.
+A \emph{necklace} in the de Bruijn graph $G_n$ is the set $\{rtl^i(w)\}_{i=1}^n$ where $w \in \N^n$, i.e., it is an equivalence class of $n$-character strings over $\N$ when strings that are rotations of each other are considered equivalent.
+A $w\in\N^n$ is called a \emph{key word} if it is larger in right-to-left lexicographic order than all of its rotations (all the words in its necklace).
+Note the resemblance of this to the notion of Lyndon words~\cite{??}, on which we will elaborate later.
+
+We are now ready to introduce another construction:
+
+\begin{algorithm}[!h]
+	Start with the one element sequence $\T{0^n}$.
+The sequence at the $i$th step is constructed by adding words to the previous sequence as follows: Let $k_i$ be the $i$th key word in right-to-left lexicographic order.
+Let $l$ be the number of leading zeros in $k_i$ ($l$ may be zero) and let $\sigma \in \N$ and $w\in\N^{n-l-1}$ be such that $k_i=0^l(\sigma+1)w$.
+Now, add the sub-sequence $\T{rtl^i(w0^l(\sigma+1))}_{i=0}^{n-1}$ between the word $\sigma w 0^l$ and its follower in the previously constructed sequence.
+	\caption{A necklace joining construction.}
+	\label{necklace-joining}
+\end{algorithm}
+
+To following proposition establishes that the above construction describes an infinite sequence of words:
+
+\begin{proposition}
+	For every $l>0$ there is $m>0$ such that for every $i>m$ the insertions of words at the $i$th step of Algorithm~\ref{necklace-joining} are all after the $l$th element of the sequence.
+\end{proposition}
+
+Let $S=\T{w_i}_{i=0}^\infty$ be the infinite sequence all whose prefixes agree with infinitely many prefixes of the finite sequences generated at the steps of Algorithm~\ref{necklace-joining}.
+Since every word is a rotation of some key word, we have that this sequence contains all the words in $\N^n$.
+Since there is a directed edge in $G_n$ from each word in this sequence to its follower, the sequence corresponds to an Hamiltonian path in $G_n$.
+The following theorem states that this path maps, by the standard correspondence described above, to the reverse of the prefer-map sequence:
+
+\begin{theorem}
+	If we take the first letter of each word in $S$ we get the sequence described in Algorithm~\ref{inf-construction}.
+\end{theorem}
+
+The
 

### 2016-12-28 paper.tex
...

@@
 $$\langle2,2,2,1,2,2,0,2,1,1,2,1,0,2,0,1,2,0,0,1,1,1,0,1,0,0,0\rangle.$$
-Note that this sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$ as substrings.
+Note that this sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$  (the words that contain the symbol $2$) as substrings.
 Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
@@
 Append the symbol $\sigma-1$  if $\sigma w$  is of the form specified in Algorithm~\ref{inf-construction}.
-Otherwise, if there is a maximal $\sigma'$ such that $\sigma'w$ is of that form, append the symbol $\sigma'$.
+Otherwise, if there is a  $\sigma'$ such that $\sigma'w$ is of that form, append the maximal such $\sigma'$.
 Otherwise, if there is no such $\sigma'$, append the symbol $\sigma$.
@@
 
-A central tool to our analysis of the sequences descibed above is an alternative formulation of the Ford sequence. For this, we need to introduce some language, as follows.
+A central tool to our analysis of the sequences descibed above is an alternative formulation of the prefer-max sequence. For this, we need to introduce some language, as follows.
 

### 2017-01-02 paper.tex
Lyndon + bibliography

@@
 
-The
+This result allows for another construction of the reversed prefer-max sequence, as follows.
+By the definition of the necklace joining construction, shown in Algorithm~\ref{necklace-joining}, one can infer that key words appear in lexicographic order and that the distance between one key words to the next is the size of the necklace of the latter.
+For a word $w\in\N^n$, let the \emph{primitive root} of $w$ be the  unique primitive (non-periodic) word $\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$.
+Since the length of the primitive root of a ket word is the length of its cycle, we get the following construction:
+
+\begin{algorithm}[!h]
+	Construct an infinite sequence of symbols by concatenating the primitive roots  of the key words of length $n$ in left-to-right lexicographic order.
+	\caption{Word concatenation construction.}
+	\label{word-concatenation}
+\end{algorithm}
+
+As the reader may expect, our result is this sequence is also the reverse of the prefer-max sequence:
+
+\begin{theorem}
+	The sequence described in Algoithm~\ref{word-concatenation} is the same sequence described in Algorithm~\ref{inf-construction}.
+\end{theorem}
+
+The last result is similar in nature to the theorem of Fredricksen and Maiorana in~\cite{Fredricksen1978} (see also~\cite{Moreno2004} and~\cite{Moreno2015}).	
+These paper contain proofs that the concatenation of Lyndon words (words that are minimal in lexicographic among their rotations) of length dividing $n$ in lexicographic order produces a de Bruijn sequence of span $n$, and they state that this word is lexicographically minimal among all
+de Bruijn sequences of span $n$.
+
+\bibliography{library}{}
+\bibliographystyle{plain}
 

### 2017-01-03 paper.tex
...
Added a reference to Ford's paper

@@
 A $k$-ary de Bruijn sequence of span $n$ is a cyclic sequence of length $k^n$ in which each $k$-ary string of length $n$ appears exactly once as
-a substring. A well known construction of such a sequence was proposed by Ford ~\cite{Ford57} as follows:
+a substring. A well known construction of such a sequence was first proposed by Ford~\cite{Ford1957} as follows:
 
@@
 By the definition of the necklace joining construction, shown in Algorithm~\ref{necklace-joining}, one can infer that key words appear in lexicographic order and that the distance between one key words to the next is the size of the necklace of the latter.
-For a word $w\in\N^n$, let the \emph{primitive root} of $w$ be the  unique primitive (non-periodic) word $\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$.
+For a word $w\in\N^n$, the \emph{primitive root} of $w$ is the  unique primitive (non-periodic) word $\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$.
 Since the length of the primitive root of a ket word is the length of its cycle, we get the following construction:
@@
 The last result is similar in nature to the theorem of Fredricksen and Maiorana in~\cite{Fredricksen1978} (see also~\cite{Moreno2004} and~\cite{Moreno2015}).	
-These paper contain proofs that the concatenation of Lyndon words (words that are minimal in lexicographic among their rotations) of length dividing $n$ in lexicographic order produces a de Bruijn sequence of span $n$, and they state that this word is lexicographically minimal among all
-de Bruijn sequences of span $n$.
+These papers show that the concatenation in lexicographic order of the Lyndon words (words that are minimal in lexicographic among their rotations) of length dividing $n$ produces a de Bruijn sequence of span $n$, and that this word is lexicographically minimal among all de Bruijn sequences of span $n$.
+In another paper~\cite{Fredricksen1970}, Fredricksen proves that (in the binary case) the prefer-max (there called Ford) sequence is the lexicographically least sequence.
+With appropriate mapping (changing the order of the letters and the direction of reading words when considering lexicographic order) our last result can be regarded as an alternative proof of the result identified by Fredricksen and Maiorana.
 

### 2017-01-03 paper.tex
...

@@
 \begin{algorithm}
-Repeatedly append the symbol $k-1$ if the word formed by the $n$ most recent symbols (padded with zeros on the left, if not enough symbols exist) is new, otherwise append $k-2$, otherwise $k-3$, etc.
+Repeatedly append the maximal symbol such that the word formed by the $n$ most recent symbols is new (in the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence).
 Stop after appending $n$ consecutive zeros.
-\caption{The prefer-max construction.}
+\caption{The prefer-max sequence.}
 \end{algorithm}
@@
 This observation lead us to look at the reverse of the prefer-max sequence.
-Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
+Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
 
@@
 While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself.
-Our result gives the first (to the best of our knowledge) efficient construction for that sequence:
+Our result gives the first (to the best of our knowledge) efficient construction of that sequence:
 
@@
 
-Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine for $\sigma'$ only symbols that are $\sigma w$ or are smaller by one than a symbol in $\sigma w$, as we will establish later in the paper.
+Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine for $\sigma'$ only symbols that are in $\sigma w$ or are smaller by one than a symbol in $\sigma w$, as we will establish later in the paper.
 The fact that this is indeed the prefer-max sequence is stated in the following theorem:

### 2017-01-03 paper.tex
Added a reference to Lyndon's paper.
...

@@
 A $w\in\N^n$ is called a \emph{key word} if it is larger in right-to-left lexicographic order than all of its rotations (all the words in its necklace).
-Note the resemblance of this to the notion of Lyndon words~\cite{??}, on which we will elaborate later.
+Note the resemblance of this to the notion of Lyndon words~\cite{Lyndon1954}, on which we will elaborate later.
 
@@
 In another paper~\cite{Fredricksen1970}, Fredricksen proves that (in the binary case) the prefer-max (there called Ford) sequence is the lexicographically least sequence.
-With appropriate mapping (changing the order of the letters and the direction of reading words when considering lexicographic order) our last result can be regarded as an alternative proof of the result identified by Fredricksen and Maiorana.
+With some mapping (changing the order of the letters and the direction of reading words when considering lexicographic order) our last result can be regarded as an alternative proof of the result identified by Fredricksen and Maiorana.
 

### 2017-01-05 paper.tex
title change
Yotam

@@
 
-\title{An Efficient Construction of the Prefer-Max Sequence and of an Infinite de Bruijn Sequence}
+\title{Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences}
 
@@
 A $k$-ary de Bruijn sequence of span $n$ is a cyclic sequence of length $k^n$ in which each $k$-ary string of length $n$ appears exactly once as
-a substring. A well known construction of such a sequence was first proposed by Ford~\cite{Ford1957} as follows:
+a substring. A well known construction of such a sequence, first proposed by Ford~\cite{Ford1957}, can be described as follows:
 
 \begin{algorithm}
-Repeatedly append the maximal symbol such that the word formed by the $n$ most recent symbols is new (in the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence).
+Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new (in the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence).
 Stop after appending $n$ consecutive zeros.
-\caption{The prefer-max sequence.}
+\caption{The $(k,n)$-prefer-max sequence.}
 \end{algorithm}
@@
 $$\langle2,2,2,1,2,2,0,2,1,1,2,1,0,2,0,1,2,0,0,1,1,1,0,1,0,0,0\rangle.$$
-Note that this sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$  (the words that contain the symbol $2$) as substrings.
+
+An obvious limitation of the above construction is, of course, that, when $n$ and $k$ grow, the amount of time and memory needed to produce the next symbol grows exponentially.
+Therefore, this construction is not practical for generating de Bruijn sequences of large alphabets and spans.
+It is used here as a mathematical definition of the sequence.
+An efficient algorithm for constructing this sequence is one of the contributions of this paper.
+
+Note that the $(n,k)$-prefer-max sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$  (the words that contain the symbol $2$) as substrings.
 Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
@@
 \begin{theorem}[Onion]
-	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$.
+	The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.
+\end{theorem}
+\begin{proof}
+	Denote the symbols of the $(n-k$)-prefer-max sequence by $s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all $i<1$.
+Let ${i_0} = \min\bigl\{i\colon (k-1) \notin \{s_{i-n+1},\dots,s_{i}\}\bigr\}$.
+	By minimality we have that $s_{{i_0}-n}=k-1$.
+Since $s_{i_0} \neq k-1$ and because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2)$ did not appear as a substring before ${i_0}$ we get, by construction, that $s_{{i_0}}=k-2$.
+This means that the exists some ${i_1}<{i_0}$ such that $s_{{i_1}-n+1}\cdots s_{{i_1}} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
+
+	Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq 0^{n-1}$.
+In particular $s_{{i_1}-n+1}\cdots s_{{i_1}} \neq 0^{n-1}(k-1)$ which means that ${i_1} > 1$.
+Therefore, $k-1  \in \{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup \{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$.
+Since the second set in this union does not contain $k-1$, we get that $s_{{i_1}-n}=k-1$.
+This leads to a contradiction because it means that $s_{{i_1}-n}\cdots s_{{i_1}-1} = s_{{i_0}-n}\cdots s_{{i_0}-1}$ which cannot happen in a de Bruijn sequence.
+This contradiction gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
+
+	The sequence is therefore as follows:
+	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,{0,\dots,0}}_{\parbox{10 em}{\scriptsize \centering{all substrings of length $n$ contain $k-1$}}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
+	To complete the proof, we need to show that all substrings of length $n$ that contain $k-1$ appear before $s_{i_0}$.
+
+	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m$ letters suffix of $w$. 
+	Because $0$ is the smallest symbol in our alphabet, we get that it is added only if all the other symbols cannot be added, i.e., when adding other symbols would generate a substring that has already being seen before.
+	%In particular, we get that $w[2..m]0$ appears as a substring in the $(n,k)$-prefer-max sequence before $w$, 
+	Since $w$ comes right before some $w[2..m]\tau$ as a window, since $\tau \geq 0$,  $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$.
+Similarly we can see that $w[2..m]0$ appears before $w[3..m]0^2$ and so on.
+	This gives us that $j_1 < j_2 < \cdots < j_n$. Note that $s_{j_1-n+1}\cdots s_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the sequence.
+
+	We will now show that if $w$ contains the symbol $k-1$ it must appear as a substring before the $i_0$'s symbol in the sequence.
+First consider the case where the last (right-most) symbol of $w$ is $k-1$.
+In this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as a substring before the $i_0$'th symbol in the sequence.
+The second case is when the last (right-most) symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$.
+
+*************
+
+%	$i^*$ %=\idx{\{0,\dots,k-2\}^n, 1}$ 
+%	be the first index such that $$of the first tuple in the $(k,n)$-prefer-max sequence that does not contains $k-1$.
+
+	Clearly, $s_{i^*}=\T{\xi_1,\dots,\xi_{n-1},k-2}$ and $s_{i^*-1}=\T{k-1,\xi_1,\dots,\xi_{n-1}}$ for some $\T{\xi_1,\dots,\xi_{n-1}}\in\{0,\dots,k-2\}^{n-1}$.
+By Observation~\ref{claim:x0 is last}, there is some $i<i^*$ such that $s_i=\T{\xi_1,\dots,\xi_{n-1},k-1}$.
+If $\T{\xi_1,\dots,\xi_{n-1}} \neq 0$ then $i \neq 1$ so we can examine the tuple $s_{i-1}$.
+By the minimality of $i^*$, the tuple $s_{i-1}$ must contain $k-1$ therefor, because $\T{\xi_1,\dots,\xi_{n-1}}\in\{0,\dots,k-2\}^{n-1}$, we must have $s_{i-1}=\T{k-1,\xi_1,\dots,\xi_{n-1}}$ which is a contradiction because it means that $s_{i-1} = s_{i^*-1}$ for some $i<i^*$.
+To avoid this contradiction we must have that  $s_i*=\T{0,\dots,0,k-2}$ and that $s_{i*-1}=\T{k-1,0,\dots,0}$
+
+	We are left to show that all the tuples that contain $k-1$ appear before $s_{i*-1}=\T{k-1,0,\dots,0}$.
+	By Observation~\ref{claim:0 follower comes after}, for all $\T{\xi_1,\dots,\xi_{n-1}}$ we have that
+	\begin{eqnarray*}
+		\idx(\T{k-1,\overbrace{0,\dots ,0}^{n-1 \text{ times}}}) 
+		& > & \idx(\T{\xi_{n-1},k-1,\overbrace{0,\dots ,0}^{n-2 \text{ times}}}) \\
+		& > & \idx(\T{\xi_{n-2},x_{n-1},\xi,\overbrace{0,\dots ,0}^{n-3 \text{ times}}}) \\    
+		& \vdots \\
+		& > &  \idx(\T{\xi_1,\dots,\xi_{n-1},k-1})
+	\end{eqnarray*}
+	This establishes that every tuple that ends with a $k-1$ at the right comes before $\T{k-1,0,\dots ,0}$.
+To see that this is also true for any tuple that contain $k-1$ at any of its coordinates, note that for such a tuple there is a tuple that comes at most $n$ indexes before it that has $k-1$ on the right.
+To complete the proof note also that all the tuples between these two tuples have $k-1$ at some coordinate that is not first from the left so we know that $\T{k-1,0,\dots ,0}$ does not come between them.
+\end{proof}
+
+%\begin{theorem}[Onion]
+%	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$.
 Furthermore, the suffix that begins with the
-	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
-	\label{thm:onion}
-\end{theorem}
+%	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
+%	\label{thm:onion}
+%\end{theorem}
+%\begin{proof}
+%	
+%\end{proof}
 
-This observation lead us to look at the reverse of the prefer-max sequence.
-Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
+This observation lead us to examine the reverse of the prefer-max sequence.
+Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
+We can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
 

### 2017-01-05 paper.tex
Proof of the Onion theorem.

@@
 	The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.
+\label{thm:onion}
 \end{theorem}
@@
 
-	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m$ letters suffix of $w$. 
+	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of $w$. 
 	Because $0$ is the smallest symbol in our alphabet, we get that it is added only if all the other symbols cannot be added, i.e., when adding other symbols would generate a substring that has already being seen before.
 	%In particular, we get that $w[2..m]0$ appears as a substring in the $(n,k)$-prefer-max sequence before $w$, 
-	Since $w$ comes right before some $w[2..m]\tau$ as a window, since $\tau \geq 0$,  $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$.
+	Since $w$ comes right before some $w[2..m]\tau$ as a window $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$.
 Similarly we can see that $w[2..m]0$ appears before $w[3..m]0^2$ and so on.
@@
 	We will now show that if $w$ contains the symbol $k-1$ it must appear as a substring before the $i_0$'s symbol in the sequence.
-First consider the case where the last (right-most) symbol of $w$ is $k-1$.
+Consider first the case where the last (right-most) symbol of $w$ is $k-1$.
 In this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as a substring before the $i_0$'th symbol in the sequence.
 The second case is when the last (right-most) symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$.
+In this case we have that $w$ appears less than $n$ steps after a window that ends with $k-1$ and the window $s_{i_0-n}\cdots s_{i_0-1}=(k-1)0^{n-1}$ does not appear in the windows between them because they all contain $k-1$ at a letter that is not  their first.
+Thus, also in this case, the window $w$ appears before the index $i_0$.
 
-*************
-
-%	$i^*$ %=\idx{\{0,\dots,k-2\}^n, 1}$ 
-%	be the first index such that $$of the first tuple in the $(k,n)$-prefer-max sequence that does not contains $k-1$.
-
-	Clearly, $s_{i^*}=\T{\xi_1,\dots,\xi_{n-1},k-2}$ and $s_{i^*-1}=\T{k-1,\xi_1,\dots,\xi_{n-1}}$ for some $\T{\xi_1,\dots,\xi_{n-1}}\in\{0,\dots,k-2\}^{n-1}$.
-By Observation~\ref{claim:x0 is last}, there is some $i<i^*$ such that $s_i=\T{\xi_1,\dots,\xi_{n-1},k-1}$.
-If $\T{\xi_1,\dots,\xi_{n-1}} \neq 0$ then $i \neq 1$ so we can examine the tuple $s_{i-1}$.
-By the minimality of $i^*$, the tuple $s_{i-1}$ must contain $k-1$ therefor, because $\T{\xi_1,\dots,\xi_{n-1}}\in\{0,\dots,k-2\}^{n-1}$, we must have $s_{i-1}=\T{k-1,\xi_1,\dots,\xi_{n-1}}$ which is a contradiction because it means that $s_{i-1} = s_{i^*-1}$ for some $i<i^*$.
-To avoid this contradiction we must have that  $s_i*=\T{0,\dots,0,k-2}$ and that $s_{i*-1}=\T{k-1,0,\dots,0}$
-
-	We are left to show that all the tuples that contain $k-1$ appear before $s_{i*-1}=\T{k-1,0,\dots,0}$.
-	By Observation~\ref{claim:0 follower comes after}, for all $\T{\xi_1,\dots,\xi_{n-1}}$ we have that
-	\begin{eqnarray*}
-		\idx(\T{k-1,\overbrace{0,\dots ,0}^{n-1 \text{ times}}}) 
-		& > & \idx(\T{\xi_{n-1},k-1,\overbrace{0,\dots ,0}^{n-2 \text{ times}}}) \\
-		& > & \idx(\T{\xi_{n-2},x_{n-1},\xi,\overbrace{0,\dots ,0}^{n-3 \text{ times}}}) \\    
-		& \vdots \\
-		& > &  \idx(\T{\xi_1,\dots,\xi_{n-1},k-1})
-	\end{eqnarray*}
-	This establishes that every tuple that ends with a $k-1$ at the right comes before $\T{k-1,0,\dots ,0}$.
-To see that this is also true for any tuple that contain $k-1$ at any of its coordinates, note that for such a tuple there is a tuple that comes at most $n$ indexes before it that has $k-1$ on the right.
-To complete the proof note also that all the tuples between these two tuples have $k-1$ at some coordinate that is not first from the left so we know that $\T{k-1,0,\dots ,0}$ does not come between them.
+	To conclude the proof we note that we established that the windows up to the index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus \{0,\dots,k-1\}^n$ and that this part of the sequence ends with $n-1$ zeros and then the next part begins with the symbol $k-2$.
+This means that from this point on the prefer-max construction acts exactly as it does when the sequence begins with $k-2$, so it constructs the $(k-1,n)$-prefer-max sequence.
 \end{proof}
 
-%\begin{theorem}[Onion]
-%	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$.
-Furthermore, the suffix that begins with the
-%	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
-%	\label{thm:onion}
-%\end{theorem}
-%\begin{proof}
-%	
-%\end{proof}
-
-This observation lead us to examine the reverse of the prefer-max sequence.
+The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence.
 Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.

### 2017-01-05 paper.tex
...

@@
 \addtokomafont{labelinglabel}{\sffamily}
+\usepackage{refcount}
 
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{reptheorem}{Theorem}
 
@@
 \caption{The $(k,n)$-prefer-max sequence.}
+\label{pref-max}
 \end{algorithm}
@@
 Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
-The first result of this paper, that we call the Onion lemma, is that this is not a coincidence:
+The first result of this paper, that we call the Onion theorem, is that this is not a coincidence:
 
@@
 \end{theorem}
-\begin{proof}
-	Denote the symbols of the $(n-k$)-prefer-max sequence by $s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all $i<1$.
-Let ${i_0} = \min\bigl\{i\colon (k-1) \notin \{s_{i-n+1},\dots,s_{i}\}\bigr\}$.
-	By minimality we have that $s_{{i_0}-n}=k-1$.
-Since $s_{i_0} \neq k-1$ and because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2)$ did not appear as a substring before ${i_0}$ we get, by construction, that $s_{{i_0}}=k-2$.
-This means that the exists some ${i_1}<{i_0}$ such that $s_{{i_1}-n+1}\cdots s_{{i_1}} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
-
-	Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq 0^{n-1}$.
-In particular $s_{{i_1}-n+1}\cdots s_{{i_1}} \neq 0^{n-1}(k-1)$ which means that ${i_1} > 1$.
-Therefore, $k-1  \in \{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup \{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$.
-Since the second set in this union does not contain $k-1$, we get that $s_{{i_1}-n}=k-1$.
-This leads to a contradiction because it means that $s_{{i_1}-n}\cdots s_{{i_1}-1} = s_{{i_0}-n}\cdots s_{{i_0}-1}$ which cannot happen in a de Bruijn sequence.
-This contradiction gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
-
-	The sequence is therefore as follows:
-	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,{0,\dots,0}}_{\parbox{10 em}{\scriptsize \centering{all substrings of length $n$ contain $k-1$}}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
-	To complete the proof, we need to show that all substrings of length $n$ that contain $k-1$ appear before $s_{i_0}$.
-
-	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of $w$. 
-	Because $0$ is the smallest symbol in our alphabet, we get that it is added only if all the other symbols cannot be added, i.e., when adding other symbols would generate a substring that has already being seen before.
-	%In particular, we get that $w[2..m]0$ appears as a substring in the $(n,k)$-prefer-max sequence before $w$, 
-	Since $w$ comes right before some $w[2..m]\tau$ as a window $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$.
-Similarly we can see that $w[2..m]0$ appears before $w[3..m]0^2$ and so on.
-	This gives us that $j_1 < j_2 < \cdots < j_n$. Note that $s_{j_1-n+1}\cdots s_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the sequence.
-
-	We will now show that if $w$ contains the symbol $k-1$ it must appear as a substring before the $i_0$'s symbol in the sequence.
-Consider first the case where the last (right-most) symbol of $w$ is $k-1$.
-In this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as a substring before the $i_0$'th symbol in the sequence.
-The second case is when the last (right-most) symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$.
-In this case we have that $w$ appears less than $n$ steps after a window that ends with $k-1$ and the window $s_{i_0-n}\cdots s_{i_0-1}=(k-1)0^{n-1}$ does not appear in the windows between them because they all contain $k-1$ at a letter that is not  their first.
-Thus, also in this case, the window $w$ appears before the index $i_0$.
-
-	To conclude the proof we note that we established that the windows up to the index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus \{0,\dots,k-1\}^n$ and that this part of the sequence ends with $n-1$ zeros and then the next part begins with the symbol $k-2$.
-This means that from this point on the prefer-max construction acts exactly as it does when the sequence begins with $k-2$, so it constructs the $(k-1,n)$-prefer-max sequence.
-\end{proof}
 
 The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence.
-Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
+Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
 We can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
@@
 
-A central tool to our analysis of the sequences descibed above is an alternative formulation of the prefer-max sequence. For this, we need to introduce some language, as follows.
+A central tool to our analysis of the sequences described above is an alternative formulation of the prefer-max sequence. For this, we need to introduce some language, as follows.
 
@@
 \begin{theorem}
-	The sequence described in Algoithm~\ref{word-concatenation} is the same sequence described in Algorithm~\ref{inf-construction}.
+	The sequence described in Algorithm~\ref{word-concatenation} is the same sequence described in Algorithm~\ref{inf-construction}.
 \end{theorem}
@@
 
+\section{A direct proof of the Onion theorem}
+
+While Theorem~\ref{thm:onion} can be proved indirectly using the fact that the necklace joining construction, described in Algorithm~\ref{necklace-joining}, gives the reverse of the pref-max construction, described in Algorithm~\ref{pref-max}, we bring here a direct proof that uses only the definition of the prefer-max sequence as the sequence generated by Algorithm~\ref{pref-max}.
+The main reason for this choice is because we view this observation as the starting point of our exploration so we do not want its proof to depend on the other results.
+
+\setcounterref{reptheorem}{thm:onion}
+\addtocounter{reptheorem}{-1}
+\begin{reptheorem}[Onion]
+	The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.
+\end{reptheorem}
+\begin{proof}
+	Denote the symbols of the $(n-k$)-prefer-max sequence by $s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all $i<1$.
+Let ${i_0} = \min\bigl\{i\colon (k-1) \notin \{s_{i-n+1},\dots,s_{i}\}\bigr\}$.
+	By minimality we have that $s_{{i_0}-n}=k-1$.
+Since $s_{i_0} \neq k-1$ and because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2)$ did not appear as a substring before ${i_0}$ (it does not contain the symbol $k-1$) we get, by construction, that $s_{{i_0}}=k-2$.
+This means that there exists some ${i_1}<{i_0}$ such that $s_{{i_1}-n+1}\cdots s_{{i_1}} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
+
+	Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq 0^{n-1}$.
+In particular $s_{{i_1}-n+1}\cdots s_{{i_1}} \neq 0^{n-1}(k-1)$ which means that ${i_1} > 1$.
+Therefore, $k-1  \in \{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup \{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$.
+Since the second set in this union does not contain $k-1$, we get that $s_{{i_1}-n}=k-1$.
+This leads to a contradiction because it means that $s_{{i_1}-n}\cdots s_{{i_1}-1} = s_{{i_0}-n}\cdots s_{{i_0}-1}$ which cannot happen in a de Bruijn sequence.
+This contradiction gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
+
+	The sequence is therefore as follows:
+	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,{0,\dots,0}}_{\parbox{10 em}{\scriptsize \centering{all substrings of length $n$ contain $k-1$}}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
+	To complete the proof, we need to show that all substrings of length $n$ that contain $k-1$ appear before $s_{i_0}$.
+
+	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of $w$. 
+	Because $0$ is the smallest symbol in our alphabet, we get that it is added only if all the other symbols cannot be added, i.e., when adding other symbols would generate a substring that has already being seen before.
+	Since $w$ comes, as a window, right before some $w[2..m]\tau$,
+	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$. Similarly we can see that $w[2..m]0$ appears before $w[3..m]0^2$ and so on.
+	This gives us that $j_1 < j_2 < \cdots < j_n$. Note that $s_{j_1-n+1}\cdots s_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the sequence.
+
+	We will now show that if $w$ contains the symbol $k-1$ it must appear as a substring before the $i_0$'s symbol in the sequence.
+Consider first the case where the last (right-most) symbol of $w$ is $k-1$.
+In this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as a substring before the $i_0$'th symbol in the sequence.
+The second case is when the last (right-most) symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$.
+In this case we have that $w$ appears less than $n$ steps after a window that ends with $k-1$ and the window $s_{i_0-n}\cdots s_{i_0-1}=(k-1)0^{n-1}$ does not appear in the windows between them because they all contain $k-1$ at a letter that is not  their first.
+Thus, also in this case, the window $w$ appears before the index $i_0$.
+
+	To conclude the proof we note that we established that the windows up to the index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus \{0,\dots,k-1\}^n$ and that this part of the sequence ends with $n-1$ zeros and then the next part begins with the symbol $k-2$.
+This means that from this point on the prefer-max construction acts exactly as it does when the sequence begins with $k-2$ so it must constructs the $(k-1,n)$-prefer-max sequence.
+\end{proof}
+
 \bibliography{library}{}

### 2017-01-06 paper.tex
...

@@
 \newtheorem{lemma}[theorem]{Lemma}
+
 \newtheorem{reptheorem}{Theorem}
+\newenvironment{repeatedtheorem}[1]
+{
+	\setcounterref{reptheorem}{#1}
+	\addtocounter{reptheorem}{-1}
+	\begin{reptheorem}
+	}{			
+	\end{reptheorem}
+}
 
@@
 The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence.
-Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
-We can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
+Specifically, the structure identified in Theorem~\ref{thm:onion} means that, if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
+Instead, we can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
 
@@
 This is formulated in Algorithm~\ref{inf-construction}.
-We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).
+We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and comparing them lexicographically (reading each word from right to left).
 
@@
 
-\setcounterref{reptheorem}{thm:onion}
-\addtocounter{reptheorem}{-1}
-\begin{reptheorem}[Onion]
-	The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.
-\end{reptheorem}
+\begin{repeatedtheorem}{thm:onion}[Onion]
+	{The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
+\end{repeatedtheorem}
 \begin{proof}
-	Denote the symbols of the $(n-k$)-prefer-max sequence by $s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all $i<1$.
-Let ${i_0} = \min\bigl\{i\colon (k-1) \notin \{s_{i-n+1},\dots,s_{i}\}\bigr\}$.
-	By minimality we have that $s_{{i_0}-n}=k-1$.
-Since $s_{i_0} \neq k-1$ and because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2)$ did not appear as a substring before ${i_0}$ (it does not contain the symbol $k-1$) we get, by construction, that $s_{{i_0}}=k-2$.
-This means that there exists some ${i_1}<{i_0}$ such that $s_{{i_1}-n+1}\cdots s_{{i_1}} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
+	Denote the symbols of the $(n-k$)-prefer-max sequence by
+	$s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all
+	$i<1$.  For each $i\geq 1$ let $w_i=s_{i-n+1}\cdots s_i$ be the ``sliding window''
+	observed at the $i$th symbol of the sequence. 
+	The proof goes by showing that $\{w_1,\dots,w_{k^n-(k-1)^n}\} = \{0,\dots,k-1\}^n \setminus \{0,\dots,k-2\}^n$.
 
-	Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq 0^{n-1}$.
-In particular $s_{{i_1}-n+1}\cdots s_{{i_1}} \neq 0^{n-1}(k-1)$ which means that ${i_1} > 1$.
-Therefore, $k-1  \in \{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup \{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$.
-Since the second set in this union does not contain $k-1$, we get that $s_{{i_1}-n}=k-1$.
-This leads to a contradiction because it means that $s_{{i_1}-n}\cdots s_{{i_1}-1} = s_{{i_0}-n}\cdots s_{{i_0}-1}$ which cannot happen in a de Bruijn sequence.
-This contradiction gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
+	Let ${i_0} = \min\{i\colon k-1 \notin w_i\}$. 
+	By minimality, because  $s_{{i_0}-n}$ is the only symbol that is in $w_{i_0-1}$ and is not in $w_{i_0}$, 
+	we have that $s_{{i_0}-n}=k-1$. Since $s_{i_0} \neq k-1$ and
+	because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2) \notin \{w_1,\dots,w_{i_0-1}\}$ because it does not contain the symbol $k-1$, 
+	we get, by the construction of the prefer-max sequence,
+	that $s_{{i_0}}=k-2$. This means that there exists some ${i_1}<{i_0}$ such that
+	$w_{i_1} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
+
+	Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq
+	0^{n-1}$. In particular $w_{i_1} \neq 0^{n-1}(k-1)$ which
+	means that ${i_1} > 1$. Therefore, $k-1  \in w_{i_1-1}=
+	\{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup
+	\{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$. Since the second set in this union does
+	not contain $k-1$, we get that $s_{{i_1}-n}=k-1$. This leads to a contradiction
+	because it means that $w_{{i_1}-1} = w_{{i_0}-1}$ which cannot happen in a de Bruijn sequence. This contradiction
+	gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
 
 	The sequence is therefore as follows:
-	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,{0,\dots,0}}_{\parbox{10 em}{\scriptsize \centering{all substrings of length $n$ contain $k-1$}}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
-	To complete the proof, we need to show that all substrings of length $n$ that contain $k-1$ appear before $s_{i_0}$.
+	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,\overbrace{0,\dots,0}^\text{$n\text{-}1$ times}}_{\text{all the $w_i$s here contain
+				$k-1$}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
+	To complete the argument, we need to show that all substrings of length $n$ that
+	contain $k-1$ appear before $s_{i_0}$.
 
-	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that $s_{j_m-n+1}\cdots s_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of $w$. 
-	Because $0$ is the smallest symbol in our alphabet, we get that it is added only if all the other symbols cannot be added, i.e., when adding other symbols would generate a substring that has already being seen before.
+	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
+	$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$
+	letters suffix of $w$. 
+	Because $0$ is the smallest symbol in our alphabet, we get that it is added
+	only if all the other symbols cannot be added, i.e., when adding other symbols
+	would generate a substring that has already being seen before. 
 	Since $w$ comes, as a window, right before some $w[2..m]\tau$,
-	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is after $w$. Similarly we can see that $w[2..m]0$ appears before $w[3..m]0^2$ and so on.
-	This gives us that $j_1 < j_2 < \cdots < j_n$. Note that $s_{j_1-n+1}\cdots s_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the sequence.
+	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is
+	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ and
+	so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that $w_{j_1}=w$, 
+	i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
+	sequence.
 
-	We will now show that if $w$ contains the symbol $k-1$ it must appear as a substring before the $i_0$'s symbol in the sequence.
-Consider first the case where the last (right-most) symbol of $w$ is $k-1$.
-In this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as a substring before the $i_0$'th symbol in the sequence.
-The second case is when the last (right-most) symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$.
-In this case we have that $w$ appears less than $n$ steps after a window that ends with $k-1$ and the window $s_{i_0-n}\cdots s_{i_0-1}=(k-1)0^{n-1}$ does not appear in the windows between them because they all contain $k-1$ at a letter that is not  their first.
-Thus, also in this case, the window $w$ appears before the index $i_0$.
+	We will now show that if $w$ contains the symbol $k-1$ it must appear as a
+	substring before the $i_0$'s symbol in the sequence. Consider first the case
+	where the last (right-most) symbol of $w$ is $k-1$. In this case, $j_n=i_{0}-1$
+	so we have, because $j_1 < j_n$, that $w$ appears as a substring before the
+	$i_0$'th symbol in the sequence. The second case is when the last (right-most)
+	symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$. In
+	this case we have that $w$ appears less than $n$ steps after a window that ends
+	with $k-1$ and the window $w_{i_0-1}=(k-1)0^{n-1}$ does not
+	appear in the windows between them because they all contain $k-1$ at a letter
+	that is not  their first. 
+	Formally, we have that there is some $m<n$ such that 
+	$j_1-m < i_0$,  $w \in \{w_{{j_1}-m},\dots,w_{j_1-1}\}$ and 
+	$w_{i_0-1} \notin \{w_{{j_1}-m},\dots,w_{j_1-1}\}$. This gives us that, also in this 
+	case, the window $w$ appears before	the index $i_0$.
 
-	To conclude the proof we note that we established that the windows up to the index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus \{0,\dots,k-1\}^n$ and that this part of the sequence ends with $n-1$ zeros and then the next part begins with the symbol $k-2$.
-This means that from this point on the prefer-max construction acts exactly as it does when the sequence begins with $k-2$ so it must constructs the $(k-1,n)$-prefer-max sequence.
+	To conclude the proof we note that we established that the windows up to the
+	index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus
+	\{0,\dots,k-2\}^n$ and that this part of the sequence ends with $n-1$ zeros and
+	then the next part begins with the symbol $k-2$. This means that from this point
+	on the prefer-max construction acts exactly as it does when the sequence begins
+	with $k-2$ so it must constructs the $(k-1,n)$-prefer-max sequence.
 \end{proof}

### 2017-01-08 paper.tex
...

@@
 Instead, we can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
-
+1
 The second contribution of this work is then an efficient construction of this reversed sequence.
@@
 \begin{repeatedtheorem}{thm:onion}[Onion]
-	{The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
+	{The last $(k-1)^n$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
 \end{repeatedtheorem}
 \begin{proof}
-	Denote the symbols of the $(n-k$)-prefer-max sequence by
+	Denote the symbols of the $(n,k$)-prefer-max sequence by
 	$s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all

### 2017-01-08 paper.tex
...

@@
 	letters suffix of $w$. 
-	Because $0$ is the smallest symbol in our alphabet, we get that it is added
+	Because zero is the smallest symbol in our alphabet, we get that it is added by the prefer-max rule
 	only if all the other symbols cannot be added, i.e., when adding other symbols
 	would generate a substring that has already being seen before. 
-	Since $w$ comes, as a window, right before some $w[2..m]\tau$,
+	Since $w$ comes, as a window, right before a word of the form $w[2..m]\tau$ for some $\tau \geq 0$,
 	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is
-	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ and
+	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$ and
 	so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that $w_{j_1}=w$, 
@@
 	We will now show that if $w$ contains the symbol $k-1$ it must appear as a
-	substring before the $i_0$'s symbol in the sequence. Consider first the case
+	substring before the $i_0$'s symbol in the sequence, i.e., that $j_1 < i_0$. Consider first the case
 	where the last (right-most) symbol of $w$ is $k-1$. In this case, $j_n=i_{0}-1$

### 2017-01-08 paper.tex
...

@@
 \begin{algorithm}
-Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new (in the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence).
+Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new.
+In the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence.
 Stop after appending $n$ consecutive zeros.

### 2017-01-09 paper.tex
Fixed some of Gal's corrections

@@
-\documentclass{article}
-%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
+\documentclass{article} %\documentclass[letterpaper, 10 pt,
+% conference]{ieeeconf}
 
-%\IEEEoverridecommandlockouts        % This command is only needed if you want to use the \thanks command
-%\overrideIEEEmargins                        % See the \addtolength command later in the file to balance the column lengths
+%\IEEEoverridecommandlockouts        % This command is only needed if you want
+%to use the \thanks command
+%\overrideIEEEmargins                        % See the \addtolength command
+%later in the file to balance the column lengths
 
@@
 
-\usepackage{epsfig} 
-\usepackage{amsmath} 
-\usepackage{amssymb} 
-\usepackage{amsthm}  
-\usepackage{hyperref}
-\usepackage{tikz}
-\usetikzlibrary{automata,arrows,decorations.pathmorphing,decorations.markings,positioning}
-\usetikzlibrary{shapes}
-%\usepackage{balance}
-\usepackage{scrextend}
-\addtokomafont{labelinglabel}{\sffamily}
+\usepackage{epsfig} \usepackage{amsmath} \usepackage{amssymb}
+\usepackage{amsthm} \usepackage{hyperref} \usepackage{tikz}
+\usetikzlibrary{automata,arrows,decorations.pathmorphing,decorations.markings,positioning} \usetikzlibrary{shapes} %\usepackage{balance}
+\usepackage{scrextend} \addtokomafont{labelinglabel}{\sffamily}
 \usepackage{refcount}
@@
 % Theorem like env.
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{theorem}{Theorem} \newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{claim}[theorem]{Claim} \newtheorem{lemma}[theorem]{Lemma}
 
-\newtheorem{reptheorem}{Theorem}
-\newenvironment{repeatedtheorem}[1]
-{
-	\setcounterref{reptheorem}{#1}
-	\addtocounter{reptheorem}{-1}
-	\begin{reptheorem}
-	}{			
-	\end{reptheorem}
-}
+\newtheorem{reptheorem}{Theorem} \newenvironment{repeatedtheorem}[1] {
+	\setcounterref{reptheorem}{#1} \addtocounter{reptheorem}{-1} \begin{reptheorem}
+	}{ \end{reptheorem} }
 
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}     
+\theoremstyle{definition} \newtheorem{definition}[theorem]{Definition}
 \newtheorem{conjecture}[theorem]{Conjecture}
 \newtheorem{observation}[theorem]{Observation}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example} \newtheorem{remark}[theorem]{Remark}
 \newtheorem{corrolary}[theorem]{Corrolary}
@@
 
-%------------------------------------------- preamble ---------------------------
+%------------------------------------------- preamble
+%---------------------------
 
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\N}{{\mathbb{N}}}
+\newcommand{\R}{{\mathbb{R}}} \newcommand{\N}{{\mathbb{N}}}
 \newcommand{\Z}{{\mathbb{Z}}}
@@
 
-\newcommand{\T}[1]{\langle{#1}\rangle}
-\newcommand{\rr}[2]{R^{#2}({#1})}
+\newcommand{\T}[1]{\langle{#1}\rangle} \newcommand{\rr}[2]{R^{#2}({#1})}
 \newcommand{\rl}[2]{R^{-{#2}}({#1})}
@@
 
-\usepackage{amssymb} 
-\usepackage{algpseudocode,algorithm}
-\usepackage{subfigure}
+\usepackage{amssymb} \usepackage{algpseudocode,algorithm} \usepackage{subfigure}
 
-\newcommand{\nega}   [1]{\overline{#1}}
-\newcommand{\companion}{comp}
-\newcommand{\shlsame}[1]{shl\text{-}same(#1)}
-\newcommand{\shlopp} [1]{shl\text{-}opp(#1)}
-\newcommand{\shlone} [1]{shl\text{-}one(#1)}
-\newcommand{\shlzero}[1]{shl\text{-}zero(#1)}
-\newcommand{\idx}    [1]{idx(#1)}
+\newcommand{\nega}   [1]{\overline{#1}} \newcommand{\companion}{comp}
+\newcommand{\shlsame}[1]{shl\text{-}same(#1)} \newcommand{\shlopp}
+[1]{shl\text{-}opp(#1)} \newcommand{\shlone} [1]{shl\text{-}one(#1)}
+\newcommand{\shlzero}[1]{shl\text{-}zero(#1)} \newcommand{\idx}    [1]{idx(#1)}
 
@@
 
-\title{Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences}
+\title{Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn
+	Sequences}
 
@@
 
-\begin{document}
-\maketitle
+\begin{document} \maketitle
 
@@
 
-A $k$-ary de Bruijn sequence of span $n$ is a cyclic sequence of length $k^n$ in which each $k$-ary string of length $n$ appears exactly once as
-a substring. A well known construction of such a sequence, first proposed by Ford~\cite{Ford1957}, can be described as follows:
+	A $k$-ary de Bruijn sequence of span $n$ is a cyclic sequence of length $k^n$
+	in which each $k$-ary string of length $n$ appears exactly once as a substring.
+	A well known construction of such a sequence, first proposed by
+	Ford~\cite{Ford1957}, can be described as follows:
 
 	\begin{algorithm}
-Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new.
-In the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence.
-Stop after appending $n$ consecutive zeros.
+		Repeatedly append the maximal symbol over the alphabet
+		$0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new.
+		In the first $n$ steps, act as if there are $n$ invisible zeros before the
+		sequence. Stop after appending $n$ consecutive zeros. 
 		\caption{The $(k,n)$-prefer-max sequence.} 
@@
 
-An obvious limitation of the above construction is, of course, that, when $n$ and $k$ grow, the amount of time and memory needed to produce the next symbol grows exponentially.
-Therefore, this construction is not practical for generating de Bruijn sequences of large alphabets and spans.
-It is used here as a mathematical definition of the sequence.
-An efficient algorithm for constructing this sequence is one of the contributions of this paper.
+	An obvious limitation of the above construction is, of course, that, when $n$
+	and $k$ grow, the amount of time and memory needed to produce the next symbol
+	grows exponentially. Therefore, this construction is not practical for
+	generating de Bruijn sequences of large alphabets and spans. It is used here as
+	a mathematical definition of the sequence. More formally, a shift rule for a de
+	Bruijn sequence of order $n$ is a function that maps each word of length $n$ to
+	the symbol that follows that word as a substring in sequence. The above is an
+	inefficient shift rule for the prefer-max sequence. The first (to the best of
+	our knowledge) efficiently computable shift rule for the prefer-max sequence is
+	one of the contributions of this paper.
 
-Note that the $(n,k)$-prefer-max sequence begins with a prefix (the first $19$ symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$  (the words that contain the symbol $2$) as substrings.
-Note also that the rest of the sequence, after this prefix, is exactly the sequence that we would have obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
-The first result of this paper, that we call the Onion theorem, is that this is not a coincidence:
+	Note that the $(n,k)$-prefer-max sequence begins with a prefix (the first $19$
+	symbols) that contains all the words in $\{0,1,2\}^n \setminus \{0,1\}^n$  (the
+	words that contain the symbol $2$) as substrings. Note also that the rest of
+	the sequence, after this prefix, is exactly the sequence that we would have
+	obtained if we ran the construction with the alphabet $k=2$ (and the same $n$).
+	The first result of this paper, that we call the Onion theorem, is that this is
+	not a coincidence:
 
 	\begin{theorem}[Onion] 
-	The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.
+		The $(k-1,n)$-prefer-max sequence is a suffix of the
+		$(k,n)$-prefer-max sequence. 
 		\label{thm:onion}
@@
 
-The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence.
-Specifically, the structure identified in Theorem~\ref{thm:onion} means that, if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time.
-Instead, we can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
-1
-The second contribution of this work is then an efficient construction of this reversed sequence.
-This is formulated in Algorithm~\ref{inf-construction}.
-We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and comparing them lexicographically (reading each word from right to left).
+	The observation made in the last theorem directed us to examine the reverse of
+	the prefer-max sequence. Specifically, the structure identified in
+	Theorem~\ref{thm:onion} means that, if we manage to construct the sequence
+	backwards, we do not have to specify $k$ ahead of time. Instead, we can add
+	symbols forever while $k$ grows in layers: we first write $0^n$, then a word
+	whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in
+	$\{0,1,2\}^n$, and so on. The second contribution of this work is then an
+	efficient construction of this reversed sequence. This is formulated in
+	Algorithm~\ref{inf-construction}. We say that this construction is efficient
+	because each step can be computed in $O(n^2)$ operations by enumerating all the
+	$n$ rotations of $\sigma w$ and comparing them lexicographically (reading each
+	word from right to left).
 
 	\begin{algorithm}[!h] 
-	Append $n$ zeros.
-Then, repeatedly, let $\sigma w$ be the word formed by the $n$ most recent symbols.
-Append $\sigma+1$ if $(\sigma+1)w$ is of the form $u0^l$ where $0^lu$ is maximal in right-to-left lexicographic order among all of its rotations.
-If $(\sigma+1)w$ is not of that form and $\sigma w$ is, append the symbol $0$.
-Otherwise, if neither $(\sigma+1)w$ nor $(\sigma)w$ are of that form, append $\sigma$.
-	\caption{An infinite de Bruijn sequence.}
-	\label{inf-construction}
+		Append $n$ zeros. Then, repeatedly, let $\sigma w$ be the
+		word formed by the $n$ most recent symbols. Append $\sigma+1$ if $(\sigma+1)w$
+		is of the form $u0^l$ where $0^lu$ is maximal in right-to-left lexicographic
+		order among all of its rotations. If $(\sigma+1)w$ is not of that form and
+		$\sigma w$ is, append the symbol $0$. Otherwise, if neither $(\sigma+1)w$ nor
+		$(\sigma)w$ are of that form, append $\sigma$. \caption{An infinite de Bruijn
+			sequence.} \label{inf-construction} 
 	\end{algorithm}
 
-The fact that this generates the reverse of the prefer-max sequence is formulated in the following theorem:
+	The fact that this generates the reverse of the prefer-max sequence is
+	formulated in the following theorem:
 
 	\begin{theorem} 
-The first $k^n$ symbols generated by Algorithm~\ref{inf-construction} form the reverse of the sequence generated by the prefer-max construction with the parameters $k$ and $n$.	
+		The first $k^n$ symbols generated by
+		Algorithm~\ref{inf-construction} form the reverse of the sequence generated by
+		the prefer-max construction with the parameters $k$ and $n$. 
 	\end{theorem}
 
-In particular, the above theorem says that the sequence generated by Algorithm~\ref{inf-construction} is a de Bruijn sequence, i.e., that each word in $\N^n$ appears exactly once as a substring.
+	In particular, the above theorem says that the sequence generated by
+	Algorithm~\ref{inf-construction} is a de Bruijn sequence, i.e., that each word
+	in $\N^n$ appears exactly once as a substring.
 
-While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself.
-Our result gives the first (to the best of our knowledge) efficient construction of that sequence:
+	While our main focus is on analyzing the reversed sequence, we also have a
+	result about the prefer-max sequence itself. Our result gives the first (to the
+	best of our knowledge) efficiently computable shift rule for that sequence:
 
-\begin{algorithm}
-	Append $n-1$ zeros and then the symbol $k$.
-Then, repeatedly, let $\sigma w$ be the word formed by the $n$ most recent symbols.
-Append the symbol $\sigma-1$  if $\sigma w$  is of the form specified in Algorithm~\ref{inf-construction}.
-Otherwise, if there is a  $\sigma'$ such that $\sigma'w$ is of that form, append the maximal such $\sigma'$.
-Otherwise, if there is no such $\sigma'$, append the symbol $\sigma$.
+	\begin{algorithm} Append $n-1$ zeros and then the symbol $k$. Then, repeatedly,
+		let $\sigma w$ be the word formed by the $n$ most recent symbols. Append the
+		symbol $\sigma-1$ if $\sigma w$  is of the form specified in
+		Algorithm~\ref{inf-construction}. Otherwise, if there is a  $\sigma'$ such that
+		$\sigma'w$ is of that form, append the maximal such $\sigma'$. Otherwise, if
+		there is no such $\sigma'$, append the symbol $\sigma$.
 
@@
 
-Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine for $\sigma'$ only symbols that are in $\sigma w$ or are smaller by one than a symbol in $\sigma w$, as we will establish later in the paper.
-The fact that this is indeed the prefer-max sequence is stated in the following theorem:
+	Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$
+	time because it suffices to examine, as candidates for $\sigma'$, only symbols
+	that are in $\sigma w$ or are smaller by one than a symbol in $\sigma w$, as we
+	will establish later in the paper. The fact that this is indeed the prefer-max
+	sequence is stated in the following theorem:
 
-\begin{theorem}
-	The sequence generated by Algorithm~\ref{efficient-pref-max} is the prefer-max sequence with parameters $k$ and $n$.
-\end{theorem}
+	\begin{theorem} The sequence generated by Algorithm~\ref{efficient-pref-max} is
+		the prefer-max sequence with parameters $k$ and $n$. \end{theorem}
 
-A central tool to our analysis of the sequences described above is an alternative formulation of the prefer-max sequence. For this, we need to introduce some language, as follows.
+	A central tool to our analysis of the sequences described above is an
+	alternative formulation of the prefer-max sequence. For this, we need to
+	introduce some language, as follows.
 
-The $n$ dimensional infinite de Bruijn graph is the graph $G_{n}=\T{V,E}$ where $V=\N^n$ and $E=\{ \T{\sigma_1 w, w \sigma_2} \colon \sigma_1,\sigma_2\in\N, w \in \N^{n-1}\}$.
-The de Bruijn sequences, defined in the beginning of this paper, are in one-to-one correspondence with the Hamiltonian cycles in the de Bruijn graph, as follows: (1) Concatenating the first letter of each vertex in a cycle produces a de Bruijn sequence of order $n$; and (2) A cycle can be constructed from a de Bruijn sequence $\T{\sigma_1,\dots,\sigma_{2^n}}$ of order $n$ by visiting the vertex $\sigma_1\cdots\sigma_n$, then $\sigma_2\cdots\sigma_{n+1}$ and so on.
+	The $n$ dimensional infinite de Bruijn graph is the graph $G_{n}=\T{V,E}$ where
+	$V=\N^n$ and $E=\{ \T{\sigma_1 w, w \sigma_2} \colon \sigma_1,\sigma_2\in\N, w
+	\in \N^{n-1}\}$. The de Bruijn sequences, defined in the beginning of this
+	paper, are in one-to-one correspondence with the Hamiltonian cycles in the de
+	Bruijn graph, as follows: (1) Concatenating the first letter of each vertex in
+	a cycle produces a de Bruijn sequence of order $n$; and (2) A cycle can be
+	constructed from a de Bruijn sequence $\T{\sigma_1,\dots,\sigma_{2^n}}$ of
+	order $n$ by visiting the vertex $\sigma_1\cdots\sigma_n$, then
+	$\sigma_2\cdots\sigma_{n+1}$ and so on.
 
-Let $rtl(\sigma_1\sigma_2\dots\sigma_n) = \sigma_2\dots\sigma_n\sigma_1$ denote the rotation of a word to the left and let $rtl^i(w)$ denote a rotation of $i$ letters to the left.
-A \emph{necklace} in the de Bruijn graph $G_n$ is the set $\{rtl^i(w)\}_{i=1}^n$ where $w \in \N^n$, i.e., it is an equivalence class of $n$-character strings over $\N$ when strings that are rotations of each other are considered equivalent.
-A $w\in\N^n$ is called a \emph{key word} if it is larger in right-to-left lexicographic order than all of its rotations (all the words in its necklace).
-Note the resemblance of this to the notion of Lyndon words~\cite{Lyndon1954}, on which we will elaborate later.
+	Let $rtl(\sigma_1\sigma_2\dots\sigma_n) = \sigma_2\dots\sigma_n\sigma_1$ denote
+	the rotation of a word to the left and let $rtl^i(w)$ denote a rotation of $i$
+	letters to the left. A \emph{necklace} in the de Bruijn graph $G_n$ is the set
+	$\{rtl^i(w)\}_{i=1}^n$ where $w \in \N^n$, i.e., it is an equivalence class of
+	$n$-character strings over $\N$ when strings that are rotations of each other
+	are considered equivalent. A $w\in\N^n$ is called a \emph{key word} if it is
+	larger in right-to-left lexicographic order than all of its rotations (all the
+	words in its necklace).  Note the resemblance of this to the notion of Lyndon
+	words~\cite{Lyndon1954}, on which we will elaborate later.
 
@@
 	\begin{algorithm}[!h] 
-	Start with the one element sequence $\T{0^n}$.
-The sequence at the $i$th step is constructed by adding words to the previous sequence as follows: Let $k_i$ be the $i$th key word in right-to-left lexicographic order.
-Let $l$ be the number of leading zeros in $k_i$ ($l$ may be zero) and let $\sigma \in \N$ and $w\in\N^{n-l-1}$ be such that $k_i=0^l(\sigma+1)w$.
-Now, add the sub-sequence $\T{rtl^i(w0^l(\sigma+1))}_{i=0}^{n-1}$ between the word $\sigma w 0^l$ and its follower in the previously constructed sequence.
-	\caption{A necklace joining construction.}
-	\label{necklace-joining}
+		Start with the one element sequence $\T{0^n}$. The
+		sequence at the $i$th step is constructed by adding words to the previous
+		sequence as follows: Let $k_i$ be the $i$th key word in right-to-left
+		lexicographic order. Let $l$ be the number of leading zeros in $k_i$ ($l$ may
+		be zero) and let $\sigma \in \N$ and $w\in\N^{n-l-1}$ be such that
+		$k_i=0^l(\sigma+1)w$. Now, add the sub-sequence
+		$\T{rtl^i(w0^l(\sigma+1))}_{i=0}^{n-1}$ between the word $\sigma w 0^l$ and its
+		follower in the previously constructed sequence. 
+		\caption{A necklace joining construction.} \label{necklace-joining} 
 	\end{algorithm}
 
-To following proposition establishes that the above construction describes an infinite sequence of words:
+	To following proposition establishes that the above construction describes an
+	infinite sequence of words:
 
 	\begin{proposition} 
-	For every $l>0$ there is $m>0$ such that for every $i>m$ the insertions of words at the $i$th step of Algorithm~\ref{necklace-joining} are all after the $l$th element of the sequence.
+		For every $l>0$ there is $m>0$ such that for every $i>m$
+		the insertions of words at the $i$th step of Algorithm~\ref{necklace-joining}
+		are all after the $l$th element of the sequence. 
 	\end{proposition}
 
-Let $S=\T{w_i}_{i=0}^\infty$ be the infinite sequence all whose prefixes agree with infinitely many prefixes of the finite sequences generated at the steps of Algorithm~\ref{necklace-joining}.
-Since every word is a rotation of some key word, we have that this sequence contains all the words in $\N^n$.
-Since there is a directed edge in $G_n$ from each word in this sequence to its follower, the sequence corresponds to an Hamiltonian path in $G_n$.
-The following theorem states that this path maps, by the standard correspondence described above, to the reverse of the prefer-map sequence:
+	Let $S=\T{w_i}_{i=0}^\infty$ be the infinite sequence all whose prefixes agree
+	with infinitely many prefixes of the finite sequences generated at the steps of
+	Algorithm~\ref{necklace-joining}. Since every word is a rotation of some key
+	word, we have that this sequence contains all the words in $\N^n$. Since there
+	is a directed edge in $G_n$ from each word in this sequence to its follower,
+	the sequence corresponds to an Hamiltonian path in $G_n$. The following theorem
+	states that this path maps, by the standard correspondence described above, to
+	the reverse of the prefer-map sequence:
 
 	\begin{theorem} 
-	If we take the first letter of each word in $S$ we get the sequence described in Algorithm~\ref{inf-construction}.
+		If we take the first letter of each word in $S$ we get the
+		sequence described in Algorithm~\ref{inf-construction}. 
 	\end{theorem}
 
-This result allows for another construction of the reversed prefer-max sequence, as follows.
-By the definition of the necklace joining construction, shown in Algorithm~\ref{necklace-joining}, one can infer that key words appear in lexicographic order and that the distance between one key words to the next is the size of the necklace of the latter.
-For a word $w\in\N^n$, the \emph{primitive root} of $w$ is the  unique primitive (non-periodic) word $\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$.
-Since the length of the primitive root of a ket word is the length of its cycle, we get the following construction:
+	This result allows for another construction of the reversed prefer-max
+	sequence, as follows. By the definition of the necklace joining construction,
+	shown in Algorithm~\ref{necklace-joining}, one can infer that key words appear
+	in lexicographic order and that the distance between one key words to the next
+	is the size of the necklace of the latter. For a word $w\in\N^n$, the
+	\emph{primitive root} of $w$ is the  unique primitive (non-periodic) word
+	$\rho(w)$ such that $w = \rho(w)^l$ for some $l \geq 1$. Since the length of
+	the primitive root of a ket word is the length of its cycle, we get the
+	following construction:
 
 	\begin{algorithm}[!h]
-	Construct an infinite sequence of symbols by concatenating the primitive roots  of the key words of length $n$ in left-to-right lexicographic order.
-	\caption{Word concatenation construction.}
-	\label{word-concatenation}
+		Construct an infinite sequence of symbols by
+		concatenating the primitive roots of the key words of length $n$ in left-to-right lexicographic order.
+		\caption{Word concatenation construction.} \label{word-concatenation}
 	\end{algorithm}
 
-As the reader may expect, our result is this sequence is also the reverse of the prefer-max sequence:
+	As the reader may expect, our result is this sequence is also the reverse of
+	the prefer-max sequence:
 
 	\begin{theorem}
-	The sequence described in Algorithm~\ref{word-concatenation} is the same sequence described in Algorithm~\ref{inf-construction}.
+		The sequence described in Algorithm~\ref{word-concatenation} is
+		the same sequence described in Algorithm~\ref{inf-construction}. 
 	\end{theorem}
 
-The last result is similar in nature to the theorem of Fredricksen and Maiorana in~\cite{Fredricksen1978} (see also~\cite{Moreno2004} and~\cite{Moreno2015}).	
-These papers show that the concatenation in lexicographic order of the Lyndon words (words that are minimal in lexicographic among their rotations) of length dividing $n$ produces a de Bruijn sequence of span $n$, and that this word is lexicographically minimal among all de Bruijn sequences of span $n$.
-In another paper~\cite{Fredricksen1970}, Fredricksen proves that (in the binary case) the prefer-max (there called Ford) sequence is the lexicographically least sequence.
-With some mapping (changing the order of the letters and the direction of reading words when considering lexicographic order) our last result can be regarded as an alternative proof of the result identified by Fredricksen and Maiorana.
+	The last result is similar in nature to the theorem of Fredricksen and Maiorana
+	in~\cite{Fredricksen1978} (see also~\cite{Moreno2004} and~\cite{Moreno2015}).
+	These papers show that the concatenation in lexicographic order of the Lyndon
+	words (words that are minimal in lexicographic among their rotations) of length
+	dividing $n$ produces a de Bruijn sequence of span $n$, and that this word is
+	lexicographically minimal among all de Bruijn sequences of span $n$. In another
+	paper~\cite{Fredricksen1970}, Fredricksen proves that (in the binary case) the
+	prefer-max (there called Ford) sequence is the lexicographically least
+	sequence. With some mapping (changing the order of the letters and the
+	direction of reading words when considering lexicographic order) our last
+	result can be regarded as an alternative proof of the result identified by
+	Fredricksen and Maiorana.
 
-\section{A direct proof of the Onion theorem}
+	\section{Proofs}
 
-While Theorem~\ref{thm:onion} can be proved indirectly using the fact that the necklace joining construction, described in Algorithm~\ref{necklace-joining}, gives the reverse of the pref-max construction, described in Algorithm~\ref{pref-max}, we bring here a direct proof that uses only the definition of the prefer-max sequence as the sequence generated by Algorithm~\ref{pref-max}.
-The main reason for this choice is because we view this observation as the starting point of our exploration so we do not want its proof to depend on the other results.
+	While Theorem~\ref{thm:onion} can be proved indirectly using the fact that the
+	necklace joining construction, described in Algorithm~\ref{necklace-joining},
+	gives the reverse of the pref-max construction, described in
+	Algorithm~\ref{pref-max}, we bring here a direct proof that uses only the
+	definition of the prefer-max sequence as the sequence generated by
+	Algorithm~\ref{pref-max}. The main reason for this choice is because we view
+	this observation as the starting point of our exploration so we do not want its
+	proof to depend on the other results.
 
 	\begin{repeatedtheorem}{thm:onion}[Onion] 
-	{The last $(k-1)^n$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
+		The $(k-1,n)$-prefer-max sequence is a suffix of the $(k,n)$-prefer-max sequence. 
 	\end{repeatedtheorem}
-\begin{proof}
-	Denote the symbols of the $(n,k$)-prefer-max sequence by
+	\begin{proof} Denote the symbols of the $(n,k$)-prefer-max sequence by
 		$s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all
-	$i<1$.  For each $i\geq 1$ let $w_i=s_{i-n+1}\cdots s_i$ be the ``sliding window''
-	observed at the $i$th symbol of the sequence. 
-	The proof goes by showing that $\{w_1,\dots,w_{k^n-(k-1)^n}\} = \{0,\dots,k-1\}^n \setminus \{0,\dots,k-2\}^n$.
+		$i<1$.  For each $i\geq 1$ let $w_i=s_{i-n+1}\cdots s_i$ be the ``sliding
+		window'' observed at the $i$th symbol of the sequence. The proof goes by
+		showing that $\{w_1,\dots,w_{k^n-(k-1)^n}\} = \{0,\dots,k-1\}^n \setminus
+		\{0,\dots,k-2\}^n$.
 
-	Let ${i_0} = \min\{i\colon k-1 \notin w_i\}$. 
-	By minimality, because  $s_{{i_0}-n}$ is the only symbol that is in $w_{i_0-1}$ and is not in $w_{i_0}$, 
-	we have that $s_{{i_0}-n}=k-1$. Since $s_{i_0} \neq k-1$ and
-	because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2) \notin \{w_1,\dots,w_{i_0-1}\}$ because it does not contain the symbol $k-1$, 
-	we get, by the construction of the prefer-max sequence,
-	that $s_{{i_0}}=k-2$. This means that there exists some ${i_1}<{i_0}$ such that
-	$w_{i_1} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
+		Let ${i_0} = \min\{i\colon k-1 \notin w_i\}$. By minimality, because
+		$s_{{i_0}-n}$ is the only symbol that is in $w_{i_0-1}$ and is not in
+		$w_{i_0}$, we have that $s_{{i_0}-n}=k-1$. Since $s_{i_0} \neq k-1$ and
+		because $s_{{i_0}-n+1}\cdots s_{{i_0}-1} (k-2) \notin \{w_1,\dots,w_{i_0-1}\}$
+		because it does not contain the symbol $k-1$, we get, by the construction of
+		the prefer-max sequence, that $s_{{i_0}}=k-2$. This means that there exists
+		some ${i_1}<{i_0}$ such that $w_{i_1} = s_{{i_0}-n+1}\cdots s_{{i_0}-1}(k-1)$.
 
 		Assume, towards contradiction, that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} \neq
-	0^{n-1}$. In particular $w_{i_1} \neq 0^{n-1}(k-1)$ which
-	means that ${i_1} > 1$. Therefore, $k-1  \in w_{i_1-1}=
+		0^{n-1}$. In particular $w_{i_1} \neq 0^{n-1}(k-1)$ which means that ${i_1} >
+		1$. Therefore, $k-1  \in w_{i_1-1}=
 		\{s_{{i_1}-n},\dots,s_{{i_1}-1}\}=\{s_{{i_1}-n}\} \cup
 		\{s_{{i_0}-n+1},\dots,s_{{i_0}-1}\}$. Since the second set in this union does
-	not contain $k-1$, we get that $s_{{i_1}-n}=k-1$. This leads to a contradiction
-	because it means that $w_{{i_1}-1} = w_{{i_0}-1}$ which cannot happen in a de Bruijn sequence. This contradiction
-	gives us that $s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
+		not contain $k-1$, we get that $s_{{i_1}-n}=k-1$. This leads to a
+		contradiction because it means that $w_{{i_1}-1} = w_{{i_0}-1}$ which cannot
+		happen in a de Bruijn sequence. This contradiction gives us that
+		$s_{{i_0}-n+1}\cdots s_{{i_0}-1} = 0^{n-1}$.
 
 		The sequence is therefore as follows:
-	$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,\overbrace{0,\dots,0}^\text{$n\text{-}1$ times}}_{\text{all the $w_i$s here contain
-				$k-1$}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$
-	To complete the argument, we need to show that all substrings of length $n$ that
-	contain $k-1$ appear before $s_{i_0}$.
+
+		$$\underbrace{s_1,\dots,s_{i_0-n-1},k-1,\overbrace{0,\dots,0}^\text{$n\text{-}1$ times}}_{\text{all the $w_i$s here contain $k-1$}},\underbrace{k-2}_{s_{i_0}},s_{i_0+1},\dots,s_{k^n+1}$$ To complete the argument, we need to show that all substrings of length $n$ that contain $k-1$ appear before $s_{i_0}$.
 
 		For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
-	$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$
-	letters suffix of $w$. 
-	Because zero is the smallest symbol in our alphabet, we get that it is added by the prefer-max rule
-	only if all the other symbols cannot be added, i.e., when adding other symbols
-	would generate a substring that has already being seen before. 
-	Since $w$ comes, as a window, right before a word of the form $w[2..m]\tau$ for some $\tau \geq 0$,
-	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is
-	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$ and
-	so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that $w_{j_1}=w$, 
-	i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
+		$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$ letters suffix of
+		$w$. Because zero is the smallest symbol in our alphabet, we get that it is
+		added by the prefer-max rule only if all the other symbols cannot be added,
+		i.e., when adding other symbols would generate a substring that has already
+		being seen before. Since $w$ comes, as a window, right before a word of the
+		form $w[2..m]\tau$ for some $\tau \geq 0$, we have that $w[2..m]0$ comes after
+		(or is equal to) $w[2..m]\tau$ which is after $w$. Similar arguments give us
+		that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$
+		and so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that
+		$w_{j_1}=w$, i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
 		sequence.
@@
 		We will now show that if $w$ contains the symbol $k-1$ it must appear as a
-	substring before the $i_0$'s symbol in the sequence, i.e., that $j_1 < i_0$. Consider first the case
-	where the last (right-most) symbol of $w$ is $k-1$. In this case, $j_n=i_{0}-1$
-	so we have, because $j_1 < j_n$, that $w$ appears as a substring before the
-	$i_0$'th symbol in the sequence. The second case is when the last (right-most)
-	symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$. In
-	this case we have that $w$ appears less than $n$ steps after a window that ends
-	with $k-1$ and the window $w_{i_0-1}=(k-1)0^{n-1}$ does not
-	appear in the windows between them because they all contain $k-1$ at a letter
-	that is not  their first. 
-	Formally, we have that there is some $m<n$ such that 
-	$j_1-m < i_0$,  $w \in \{w_{{j_1}-m},\dots,w_{j_1-1}\}$ and 
-	$w_{i_0-1} \notin \{w_{{j_1}-m},\dots,w_{j_1-1}\}$. This gives us that, also in this 
-	case, the window $w$ appears before	the index $i_0$.
+		substring before the $i_0$'s symbol in the sequence, i.e., that $j_1 < i_0$.
+		Consider first the case where the last (right-most) symbol of $w$ is $k-1$. In
+		this case, $j_n=i_{0}-1$ so we have, because $j_1 < j_n$, that $w$ appears as
+		a substring before the $i_0$'th symbol in the sequence. The second case is
+		when the last (right-most) symbol in $w$ is not $k-1$ but there is another
+		letter in $w$ which is $k-1$. In this case we have that $w$ appears less than
+		$n$ steps after a window that ends with $k-1$ and the window
+		$w_{i_0-1}=(k-1)0^{n-1}$ does not appear in the windows between them because
+		they all contain $k-1$ at a letter that is not  their first. Formally, we have
+		that there is some $m<n$ such that $j_1-m < i_0$,  $w \in
+		\{w_{{j_1}-m},\dots,w_{j_1-1}\}$ and $w_{i_0-1} \notin
+		\{w_{{j_1}-m},\dots,w_{j_1-1}\}$. This gives us that, also in this case, the
+		window $w$ appears before	the index $i_0$.
 
@@
 		index $i_0$ contain all and only the words in $\{0,\dots,k-1\}^n \setminus
-	\{0,\dots,k-2\}^n$ and that this part of the sequence ends with $n-1$ zeros and
-	then the next part begins with the symbol $k-2$. This means that from this point
-	on the prefer-max construction acts exactly as it does when the sequence begins
-	with $k-2$ so it must constructs the $(k-1,n)$-prefer-max sequence.
+		\{0,\dots,k-2\}^n$ and that this part of the sequence ends with $n-1$ zeros
+		and then the next part begins with the symbol $k-2$. This means that from this
+		point on the prefer-max construction acts exactly as it does when the sequence
+		begins with $k-2$ so it must constructs the $(k-1,n)$-prefer-max sequence.
 	\end{proof}

### 2017-01-10 paper.tex
m --> n in the proof of the Onion theorem

@@
 
-	\begin{algorithm}
-		Repeatedly append the maximal symbol over the alphabet
+	\begin{algorithm} Repeatedly append the maximal symbol over the alphabet
 		$0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new.
 		In the first $n$ steps, act as if there are $n$ invisible zeros before the
-		sequence. Stop after appending $n$ consecutive zeros. 
-		\caption{The $(k,n)$-prefer-max sequence.} 
-		\label{pref-max} 
-	\end{algorithm}
+		sequence. Stop after appending $n$ consecutive zeros. \caption{The
+			$(k,n)$-prefer-max sequence.} \label{pref-max} \end{algorithm}
 
@@
 
-	\begin{theorem}[Onion] 
-		The $(k-1,n)$-prefer-max sequence is a suffix of the
-		$(k,n)$-prefer-max sequence. 
-		\label{thm:onion}
-	\end{theorem}
+	\begin{theorem}[Onion] The $(k-1,n)$-prefer-max sequence is a suffix of the
+		$(k,n)$-prefer-max sequence. \label{thm:onion} \end{theorem}
 
@@
 
-	\begin{algorithm}[!h] 
-		Append $n$ zeros. Then, repeatedly, let $\sigma w$ be the
+	\begin{algorithm}[!h] Append $n$ zeros. Then, repeatedly, let $\sigma w$ be the
 		word formed by the $n$ most recent symbols. Append $\sigma+1$ if $(\sigma+1)w$
@@
 		$(\sigma)w$ are of that form, append $\sigma$. \caption{An infinite de Bruijn
-			sequence.} \label{inf-construction} 
-	\end{algorithm}
+			sequence.} \label{inf-construction} \end{algorithm}
 
@@
 
-	\begin{theorem} 
-		The first $k^n$ symbols generated by
+	\begin{theorem} The first $k^n$ symbols generated by
 		Algorithm~\ref{inf-construction} form the reverse of the sequence generated by
-		the prefer-max construction with the parameters $k$ and $n$. 
-	\end{theorem}
+		the prefer-max construction with the parameters $k$ and $n$. \end{theorem}
 
@@
 		\caption{An efficient construction of the prefer-max sequence.}
-		\label{efficient-pref-max} 
-	\end{algorithm}
+		\label{efficient-pref-max} \end{algorithm}
 
@@
 
-	\begin{algorithm}[!h] 
-		Start with the one element sequence $\T{0^n}$. The
+	\begin{algorithm}[!h] Start with the one element sequence $\T{0^n}$. The
 		sequence at the $i$th step is constructed by adding words to the previous
@@
 		$\T{rtl^i(w0^l(\sigma+1))}_{i=0}^{n-1}$ between the word $\sigma w 0^l$ and its
-		follower in the previously constructed sequence. 
-		\caption{A necklace joining construction.} \label{necklace-joining} 
-	\end{algorithm}
+		follower in the previously constructed sequence. \caption{A necklace joining
+			construction.} \label{necklace-joining} \end{algorithm}
 
@@
 
-	\begin{proposition} 
-		For every $l>0$ there is $m>0$ such that for every $i>m$
+	\begin{proposition} For every $l>0$ there is $m>0$ such that for every $i>m$
 		the insertions of words at the $i$th step of Algorithm~\ref{necklace-joining}
-		are all after the $l$th element of the sequence. 
-	\end{proposition}
+		are all after the $l$th element of the sequence. \end{proposition}
 
@@
 
-	\begin{theorem} 
-		If we take the first letter of each word in $S$ we get the
-		sequence described in Algorithm~\ref{inf-construction}. 
-	\end{theorem}
+	\begin{theorem} If we take the first letter of each word in $S$ we get the
+		sequence described in Algorithm~\ref{inf-construction}. \end{theorem}
 
@@
 
-	\begin{algorithm}[!h]
-		Construct an infinite sequence of symbols by
-		concatenating the primitive roots of the key words of length $n$ in left-to-right lexicographic order.
-		\caption{Word concatenation construction.} \label{word-concatenation}
-	\end{algorithm}
+	\begin{algorithm}[!h] Construct an infinite sequence of symbols by
+		concatenating the primitive roots of the key words of length $n$ in
+		left-to-right lexicographic order. \caption{Word concatenation construction.}
+		\label{word-concatenation} \end{algorithm}
 
@@
 
-	\begin{theorem}
-		The sequence described in Algorithm~\ref{word-concatenation} is
-		the same sequence described in Algorithm~\ref{inf-construction}. 
-	\end{theorem}
+	\begin{theorem} The sequence described in Algorithm~\ref{word-concatenation} is
+		the same sequence described in Algorithm~\ref{inf-construction}. \end{theorem}
 
@@
 
-	\begin{repeatedtheorem}{thm:onion}[Onion] 
-		The $(k-1,n)$-prefer-max sequence is a suffix of the $(k,n)$-prefer-max sequence. 
-	\end{repeatedtheorem}
+	\begin{repeatedtheorem}{thm:onion}[Onion] The $(k-1,n)$-prefer-max sequence is
+		a suffix of the $(k,n)$-prefer-max sequence. \end{repeatedtheorem}
 	\begin{proof} Denote the symbols of the $(n,k$)-prefer-max sequence by
@@
 		being seen before. Since $w$ comes, as a window, right before a word of the
-		form $w[2..m]\tau$ for some $\tau \geq 0$, we have that $w[2..m]0$ comes after
-		(or is equal to) $w[2..m]\tau$ which is after $w$. Similar arguments give us
-		that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$
+		form $w[2..n]\tau$ for some $\tau \geq 0$, we have that $w[2..n]0$ comes after
+		(or is equal to) $w[2..n]\tau$ which is after $w$. Similar arguments give us
+		that $w[2..n]0$ appears before $w[3..n]0^2$ which appears before $w[4..n]0^3$
 		and so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that
@@
 
-	\bibliography{library}{} 
-	\bibliographystyle{plain}
+	\bibliography{library}{} \bibliographystyle{plain}
 
